---
title: "Spike-and-Slab GOLAZO stan timings"
author: "Jack Jewson"
date: "25/07/2022"
output: html_document
---

This notebook provides code to undertake the timings comparison of stan's implementation of the Network SS and the Network GLASSO  outlined in Section D of the paper 

# Preliminaries {.tabset}

## working directory

```{r working_directory, include=TRUE,echo=TRUE, eval=TRUE,cache=FALSE}
data_dir <- '/home/usuario/Documents/Barcelona_Yr1/GraphicalModels_NetworkData/LiLicode/paper_code_github/'
setwd(data_dir)
```

## Packages

```{r packages, include=TRUE,echo=TRUE, eval=TRUE,cache=FALSE}
library(polynom)
library(MASS)
library(misc3d)
library(LaplacesDemon)
library(vioplot)
library(rjson)
library(data.table)
library(xtable)
library(knitr)

library(rstan); 
rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores())

```

## Functions 

```{r functions, include=TRUE,echo=TRUE, eval=TRUE,cache=TRUE}

to_triangular <- function(y_basis, K) {
  ## could check rows(y) = K * (K - 1) / 2
  ## matrix[K, K] y; // code works but throws warning
  y <- matrix(0, nrow = K, ncol = K);   
  pos = 1
  for(i in 2:K) {
    for(j in 1:(i-1)) {
      y[i, j] <- y_basis[pos]
      pos <- pos + 1
    }
  }
  return(y)
}

from_triangular <- function(y_tri) {
  ## could check rows(y) = K * (K - 1) / 2
  ## matrix[K, K] y; // code works but throws warning
  K <- nrow(y_tri)
  y_basis <- rep(0, K * (K - 1) / 2)   
  pos = 1
  for(i in 2:K) {
    for(j in 1:(i-1)) {
      y_basis[pos] <- y_tri[i, j]
      pos <- pos + 1
    }
  }
  return(y_basis)
}

dlaplace_SS <- function(rho, s0, eta0, eta1, eta2){
  w <- 1/(1+ exp(-eta2))
  return((1-w)*dlaplace(rho, 0, s0) + w*dlaplace(rho, eta0, s0*(1+exp(-eta1))))
}

```

## Hyparameters

### s0 (spike-scale)

This will be fixed for eveything 

```{r eliciting_spike, include=TRUE,echo=TRUE, eval=TRUE,cache=TRUE}

thresh <- 0.01

prob_thresh <- 0.95
spike_scale_optim <- optimize(f = function(s0){abs((plaplace(thresh, 0, s0) - plaplace(-thresh, 0, s0)) - prob_thresh)}, lower = 0, upper = 1)
spike_scale_optim$objective

spike_scale_set <- spike_scale_optim$minimum
spike_scale_set

s0 <- spike_scale_set

threshold <- function(Theta_mat, threshold){
  return(Theta_mat*(abs(Theta_mat) >= threshold))
}

```

### MCMC Iterations

```{r MCMCIterations, include=TRUE,echo=TRUE, eval=TRUE,cache=TRUE}

warmup <- 2000
iterations <- warmup + 2000


```

# Data Loading

```{r Experiment_Settings, include=TRUE,echo=TRUE, eval=TRUE,cache=TRUE}

p <- 10 # dimension of observations/number of ocunties
N <- 10 # number of repeats
n <- 100 # numbe rof observations/time points

n_max <- 2000 # largest sample size considered

```

```{r Data_Load, include=TRUE,echo=TRUE, eval=TRUE,cache=TRUE}

data_folder <- "Data/Simulations/"
#n_sims <- 10
#p <- 10

# Extract theta_true, mu_true, n_obs, As (the same for every file, using sim0)
data_path <- paste0(data_dir,data_folder,"sim0_p", p, "_n2000.json")
data <- fromJSON(file=data_path)
var_names <- paste0('p', seq(1,p))

#theta_true <- data.matrix(as.data.frame(data.table::transpose(data['theta_true']$theta_true), col.names = var_names))
Theta <- data.matrix(as.data.frame(data.table::transpose(data['theta_true']$theta_true), col.names = var_names))

A_semidep85 <- data.matrix(as.data.frame(data.table::transpose(data['A_semi_dep85']$A_semi_dep85), col.names = var_names))
A_scaled_semidep85 <- data.matrix(as.data.frame(data.table::transpose(data['A_scaled_semi_dep85']$A_scaled_semi_dep85), col.names = var_names))


mu_true <- data.matrix(as.data.frame(t(data['mu_true']$mu_true)))
names(mu_true) <- var_names

n_obs <- data['n']$n

# Create list of extracted Y for each simulation
Y_list <- list()

for (i in seq(0,N-1)){
  data_path <- paste0(data_dir,data_folder,"sim", i, "_p", p, "_n2000.json")
  data <- fromJSON(file=data_path)
  Y_list[[i+1]] <- data.matrix(as.data.frame(data.table::transpose(data['Y']$Y), col.names = var_names))
}

rm(data)

Theta_zeros <- Theta[lower.tri(Theta)]
TN <- sum(Theta_zeros == 0)
TP <- sum(Theta_zeros != 0)
```


# Network SS - A-semidep85 {.tabset}

## Prior Specification 

```{r GOLAZO_semidep85A_SS_prior_specification, include=TRUE,echo=TRUE, eval=TRUE,cache=TRUE}

s0 <- 0.003
spike_scale_set <- 0.003

m_00_set_GOLAZO_SS_semidep85A <- 0
s_00_set_GOLAZO_SS_semidep85A <- 0.126
m_01_set_GOLAZO_SS_semidep85A <- -2.197
s_01_set_GOLAZO_SS_semidep85A <- 0.4
m_02_set_GOLAZO_SS_semidep85A <- -2.444
s_02_set_GOLAZO_SS_semidep85A <- 1.944

```

## Stan files

```{r GOLAZO_semidep85A_SS_stan_files, include=TRUE,echo=TRUE, eval=TRUE,cache=TRUE}

setwd(data_dir)

#Learn_Beta_Bayesian_GOLAZO_partialCorrelation_SS_Indicator_stan <- stan_model(file = "Network_Spike_and_Slab/stan/Network_SS.stan")
Learn_Beta_Bayesian_GOLAZO_partialCorrelation_SS_Indicator_stan <- stan_model(file = "Network_Spike_and_Slab/stan/Network_SS_muFixed.stan")

```

## Inference

```{r GOLAZO_semidep85A_SS, include=TRUE,echo=TRUE, eval=TRUE,cache=TRUE}

Rho_hat_GOLAZO_semidep85A_SS_bayes <- array(NA, dim = c(p, p, N))

eta0_MAP_GOLAZO_semidep85A_SS_bayes <- matrix(NA, nrow = N, ncol = 2)
eta1_MAP_GOLAZO_semidep85A_SS_bayes <- matrix(NA, nrow = N, ncol = 2)
eta2_MAP_GOLAZO_semidep85A_SS_bayes <- matrix(NA, nrow = N, ncol = 2)

Bayesian_GOLAZO_semidep85A_partialCorrelation_SS_Indicator_returncode <- rep(NA, N)

stan_time_GOLAZO_semidep85A_SS <- matrix(NA, nrow = N, ncol = 2)
ESS_GOLAZO_semidep85A_SS <- matrix(NA, nrow = N, ncol = 2) # etas and rhos

time_GOLAZO_semidep85A_SS_bayes.start <- Sys.time()
for(j in 1:N){
  
  Learn_Beta_Bayesian_GOLAZO_semidep85A_partialCorrelation_SS_Indicator_data <- 
    list(n=n, p=p, Y = Y_list[[j]][1:n,], mu = rep(0, p), mu_m = 0, mu_s = 1
           , eta0_p1 = m_00_set_GOLAZO_SS_semidep85A
           , eta0_p2 = s_00_set_GOLAZO_SS_semidep85A
           , eta1_p1 = m_01_set_GOLAZO_SS_semidep85A
           , eta1_p2 = s_01_set_GOLAZO_SS_semidep85A
           , eta2_p1 = m_02_set_GOLAZO_SS_semidep85A
           , eta2_p2 = s_02_set_GOLAZO_SS_semidep85A
           , s0 = spike_scale_set
           , A = A_scaled_semidep85) 
  
  Learn_Beta_Bayesian_GOLAZO_semidep85A_partialCorrelation_SS_Indicator <- sampling(object = Learn_Beta_Bayesian_GOLAZO_partialCorrelation_SS_Indicator_stan, 
        data = Learn_Beta_Bayesian_GOLAZO_semidep85A_partialCorrelation_SS_Indicator_data, 
        warmup = warmup, iter = iterations, chains = 1
        , init = list(c1 = list(#mu = rep(0, p), 
                     tilde_Rho_basis = rep(0, p*(p-1)/2), 
           sqrt_theta_ii = rep(1, p),
                    tilde_eta0 = c(0, 0),
                    tilde_eta1 = c(0, 0),
                    tilde_eta2 = c(0, 0),
                 u_basis = rep(0.5, p*(p-1)/2)
        ))
  )
  
  stan_time_GOLAZO_semidep85A_SS[j,] <- get_elapsed_time(Learn_Beta_Bayesian_GOLAZO_semidep85A_partialCorrelation_SS_Indicator)

  Learn_Beta_Bayesian_GOLAZO_semidep85A_partialCorrelation_SS_Indicator_params <- extract(Learn_Beta_Bayesian_GOLAZO_semidep85A_partialCorrelation_SS_Indicator)
  
  ESS_GOLAZO_semidep85A_SS[j,] <- c(mean(summary(Learn_Beta_Bayesian_GOLAZO_semidep85A_partialCorrelation_SS_Indicator)$summary[p + 1:6,"n_eff"]), mean(summary(Learn_Beta_Bayesian_GOLAZO_semidep85A_partialCorrelation_SS_Indicator)$summary[p + 6 + 2*p*(p-1)/2 + 2*p^2 + 1:(p^2),"n_eff"], na.rm = TRUE))
  
  eta0_MAP_GOLAZO_semidep85A_SS_bayes[j,] <- colMeans(Learn_Beta_Bayesian_GOLAZO_semidep85A_partialCorrelation_SS_Indicator_params$eta0) 
  eta1_MAP_GOLAZO_semidep85A_SS_bayes[j,] <- colMeans(Learn_Beta_Bayesian_GOLAZO_semidep85A_partialCorrelation_SS_Indicator_params$eta1) 
  eta2_MAP_GOLAZO_semidep85A_SS_bayes[j,] <- colMeans(Learn_Beta_Bayesian_GOLAZO_semidep85A_partialCorrelation_SS_Indicator_params$eta2) 
  Rho_hat_GOLAZO_semidep85A_SS_bayes[,,j] <- threshold(apply(Learn_Beta_Bayesian_GOLAZO_semidep85A_partialCorrelation_SS_Indicator_params$Rho, c(2, 3), mean), thresh)

  
  cat("GOLAZO-semidep85A_bayes", "n", n , "Repeat", j, "done", "\n") 
}
time_GOLAZO_semidep85A_SS_bayes.end <- Sys.time()

```

## Results Summary

```{r GOLAZO_semidep85A_SS_results, include=TRUE,echo=TRUE, eval=TRUE,cache=FALSE}

time_GOLAZO_semidep85A_SS_bayes1 <- time_GOLAZO_semidep85A_SS_bayes.end - time_GOLAZO_semidep85A_SS_bayes.start
time_GOLAZO_semidep85A_SS_bayes <- time_GOLAZO_semidep85A_SS_bayes1/N
time_GOLAZO_semidep85A_SS_bayes

stan_time_GOLAZO_semidep85A_SS
mean(stan_time_GOLAZO_semidep85A_SS[,1] + stan_time_GOLAZO_semidep85A_SS[,2])

colMeans(ESS_GOLAZO_semidep85A_SS)

```


# Frequentist GOLAZO Timings

## Packages

```{r packages2, include=TRUE,echo=TRUE, eval=TRUE,cache=FALSE}

library(devtools)
#install_github("pzwiernik/golazo", build_vignettes=TRUE)
library(golazo)
#source('Network_GLASSO/GOLAZO_function.R')


```

## Functions 

```{r functions2, include=TRUE,echo=TRUE, eval=TRUE,cache=TRUE}

ebic_eval <- function(n, R, U, ebic.gamma, edge.tol){
  res <- golazo(R, L = -U, U = U, verbose = FALSE)
  K <- res$K
  KR <- stats::cov2cor(K)         #to make edge count independend of scalings
  nedg <- length(which(abs(KR[upper.tri(abs(KR), diag = FALSE)]) > edge.tol))
  ## p is the dimensions of R I think - this should be fine but isn't great code!
  ebic <- -(n)*(log(det(K)) - sum(R*K)) + nedg * (log(n) + 4 * ebic.gamma * log(p))
  return(ebic)   
}

ebic_eval_network <- function(n, R, A, beta0, beta1, ebic.gamma, edge.tol){
  U <- exp(beta0 + beta1*A)  
  diag(U) <- 0
  return(ebic_eval(n, R, U, ebic.gamma, edge.tol))
}

ebic_eval_two_networks <- function(n, R, A1, A2, beta0, beta1, beta2, ebic.gamma, edge.tol){
   U <- exp(beta0 + beta1*A1 + beta2*A2)
   diag(U) <- 0
   return(ebic_eval(n, R, U, ebic.gamma, edge.tol))
}


standardise_network_matrix_tri <- function(A) {
  p <- nrow(A)
  
  A_tri <- A[upper.tri(A)]
  bar_A_tri <- mean(A_tri)
  S2_A_tri <- 1/length(A_tri)*sum((A_tri - bar_A_tri)^2)
  
  return((A - bar_A_tri)/sqrt(S2_A_tri))
}

## Turning the correlation matrix given by the golazo function back to a covariance matrix, useful in out-of-sample-llh
cor2cov <- function(Theta_cor, sigma2_vect){
  # Theta_cor is correlation matrix, sqrt(sigma2_vect) is the standard deviations of each variable
  p <- nrow(Theta_cor)
  Theta_cov <- matrix(NA, nrow = p, ncol = p)
  for(i in 1:p){
    Theta_cov[, i] <- Theta_cor[,i]*sqrt(sigma2_vect[i])*sqrt(sigma2_vect)   
  }
  return(Theta_cov)
}


threshold <- function(Rho_mat, threshold){
  return(Rho_mat*(abs(Rho_mat) >= threshold))
}



## No Network matrix
beta0_max_GLASSO <- function(R){
  return(log(max(abs(R - diag(diag(R))))))## check we can irgnore diags
  #return(log(max(max(diag(R)^2) - abs(R)))) ## Piotr's updated bound!
}


```

## Hyperparameters

```{r GOLAZO_hyperparameters, include=TRUE,echo=TRUE, eval=TRUE,cache=TRUE}
## Hyperparameters ##
ebic.gamma <- 0    # when equals to 0, it's BIC; when equals to 0.5, it's EBIC
edge.tol   <- 1e-6   

```

## Inference

```{r GOLAZO_semidep85A, include=TRUE,echo=TRUE, eval=TRUE,cache=TRUE}

Rho_squared_error_freq <- rep(0, N) 

Ps <- rep(0, N)
Ns <- rep(0, N)


ebic_eval_optim_GOLAZO_A_semidep <- rep(NA, N)


false_positives_freq <- rep(0, N)  
false_negatives_freq <- rep(0, N)   

beta <- matrix(NA, nrow = N, ncol = 2)

beta0_grid_length <- 50
beta0_grid_max <- 2
beta0_grid_min <- -5

beta0_grid <- seq(beta0_grid_min, beta0_grid_max, length.out = beta0_grid_length - 1)
beta0_grid <- sort(c(beta0_grid, 0)) 

beta1_grid_length <- 50
beta1_grid_max <- 2
beta1_grid_min <- -2.5

beta1_grid <- seq(beta1_grid_min, beta1_grid_max, length.out = beta1_grid_length - 1)
beta1_grid <- sort(c(beta1_grid, 0)) 


timer_GOLAZO_semidepA.start <- Sys.time()
for(j in 1:N){
  
  #### Estimating beta ####
   R <- stats::cov2cor(cov(Y_list[[j]][1:n,]))   # cov2cor convert covariance matrix to correlation matrix
  
  beta_optimise <- matrix(NA, nrow = beta0_grid_length, ncol = beta1_grid_length)
  for(b0 in 1:beta0_grid_length){
    for(b1 in 1:beta1_grid_length){
      #cat("b0 = ", b0, ", b1 = ", b1, "\n")
      try(beta_optimise[b0, b1] <- ebic_eval_network(n, R, A_scaled_semidep85, beta0 = beta0_grid[b0], beta1 = beta1_grid[b1], ebic.gamma, edge.tol))
    }
  }
  
  min_coord <- which(beta_optimise== min(beta_optimise, na.rm = TRUE), arr.ind = TRUE)
  
  dim(min_coord) <- c(length(min_coord)/2, 2)
  beta[j, 1] <- mean(beta0_grid[min_coord[,1]])
  beta[j, 2] <- mean(beta1_grid[min_coord[,2]])
  
  # Saving the EBIC 
  ebic_eval_optim_GOLAZO_A_semidep[j] <- min(beta_optimise, na.rm = TRUE) 
  
  ## use the optimal beta0 and beta1
  U <- exp(beta[j,1] + beta[j,2]*A_scaled_semidep85) 
  diag(U) <- 0
  
  res <- golazo(R,-U, U, verbose=FALSE)

  
  Rho_hat_GOLAZO_semidepA_freq <- threshold(cov2cor(res$K), edge.tol)
  Rho_squared_error_freq[j] <- sum((Rho_hat_GOLAZO_semidepA_freq - cov2cor(Theta))^2)
  Rho_hat_zeros_freq <- Rho_hat_GOLAZO_semidepA_freq[lower.tri(Rho_hat_GOLAZO_semidepA_freq)]
  
  
  false_positives_freq[j] <- sum((Rho_hat_zeros_freq != 0) & (Theta_zeros == 0))  
  false_negatives_freq[j] <- sum((Rho_hat_zeros_freq == 0) & (Theta_zeros != 0))
  
  Ps[j] <-  sum(Rho_hat_GOLAZO_semidepA_freq != 0)
  Ns[j] <-  sum(Rho_hat_GOLAZO_semidepA_freq == 0)
 
  cat("GOLAZO-semidepA_freq", "n", n , "Repeat", j, "done", "\n") 
}
timer_GOLAZO_semidepA.end <- Sys.time()

```

## Results Summary

```{r GOLAZO_semidep85A_results, include=TRUE,echo=TRUE, eval=TRUE,cache=FALSE}


time_GOLAZO_semidepA1 <- timer_GOLAZO_semidepA.end - timer_GOLAZO_semidepA.start
time_GOLAZO_semidepA  <- round(time_GOLAZO_semidepA1/N, 3)
time_GOLAZO_semidepA 

time_GOLAZO_semidepA * 60

total_negatives <- sum(Theta_zeros ==0)
total_positives <- sum(Theta_zeros !=0)

MSE_GOLAZO_semidepA_freq <- round(mean(Rho_squared_error_freq), 3) 
FPR_GOLAZO_semidepA_freq  <- round(mean(false_positives_freq/total_negatives), 3)       
FNR_GOLAZO_semidepA_freq  <- round(mean(false_negatives_freq/total_positives), 3)
TCR_GOLAZO_semidepA_freq  <- round(sum((false_positives_freq == 0) & (false_negatives_freq == 0))/N, 3)  


beta_GOLAZO_semidepA_freq   <- beta
m_beta_GOLAZO_semidepA_freq <-round(colMeans(beta_GOLAZO_semidepA_freq), 3)
m_ebic_eval_optim_GOLAZO_A_semidep <- round(mean(ebic_eval_optim_GOLAZO_A_semidep), 3)

MSE_GOLAZO_semidepA_freq
FPR_GOLAZO_semidepA_freq
FNR_GOLAZO_semidepA_freq
TCR_GOLAZO_semidepA_freq


beta_GOLAZO_semidepA_freq 
m_beta_GOLAZO_semidepA_freq

ebic_eval_optim_GOLAZO_A_semidep
m_ebic_eval_optim_GOLAZO_A_semidep

FDiscR_GOLAZO_A_semidep <- round(mean(false_positives_freq / Ps), 3) 
FNonDiscR_GOLAZO_A_semidep <- round(mean(false_negatives_freq /Ns), 3)


FDiscR_GOLAZO_A_semidep
FNonDiscR_GOLAZO_A_semidep

```
