---
title: "priorSpecification Network Spike-and-Slab"
author: "Jack Jewson"
date: "30 March 2022"
output: html_document
---

This notebook provides code to undertake the prior elicitation exercise outlined in Section A.3 of the paper 

# Packages

```{r packages, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE}

library(LaplacesDemon)

library(rjson)
library(data.table)
library(xtable)
library(knitr)

library(readr)
```

## Functions

```{r corr_mat_functions, include=TRUE,echo=TRUE, eval=TRUE,cache=TRUE}


corrType_mat_fill <- function(p, values){
  if(length(values) != (p*(p-1)/2)){return(paste("NOT ENOUGH VALUES"))}
  rho <- diag(0.5, p)
  rho[upper.tri(rho, diag = FALSE)] <- values
  rho <- rho + t(rho)
  return(rho)
}

#corrType_mat_fill(4, runif(6))

is.corrMat <- function(rho){
  maxVal <- (max(abs(rho)) <= 1)
  PD <- min(eigen(rho)$values) > 0
  return(as.numeric(maxVal & PD))
}

```

## Eliciting the spike

Here we also define a Thresholding function

```{r eliciting_NEWspike, include=TRUE,echo=TRUE, eval=TRUE,cache=TRUE}

thresh <- 0.01

prob_thresh <- 0.95
spike_scale_optim <- optimize(f = function(s0){abs((plaplace(thresh, 0, s0) - plaplace(-thresh, 0, s0)) - prob_thresh)}, lower = 0, upper = 1)
spike_scale_optim$objective

spike_scale_set <- spike_scale_optim$minimum
spike_scale_set

s0 <- spike_scale_set

threshold <- function(Theta_mat, threshold){
  return(Theta_mat*(abs(Theta_mat) >= threshold))
}

```

# Spike-and-Slab

For Spike-and-Slab GLASSO we have 

$$
\begin{align}
\rho_{jk} &\sim (1 - w_{jk})\textrm{DExp}(0, s_0) + 
               w_{jk}\textrm{DExp}(\eta_{0}, s_{jk}),\\
w_{jk} &= \frac{1}{1 + \exp(-\eta_{2}a_{jk}))}, \quad s_{jk} = s_0(1 + \exp(-\eta_{1}a_{jk}))\\
\eta_{00} &\sim \mathcal{N}(m_{0}, g_{0}^2), \quad\eta_{0q} \sim \mathcal{N}(0, g_{0}^2)\\
\eta_{10} &\sim \mathcal{N}(m_{1}, g_{1}^2), \quad\eta_{1q} \sim \mathcal{N}(0, g_{0}^2)\\
\eta_{20} &\sim \mathcal{N}(m_{2}, g_{2}), \quad\eta_{2q} \sim \mathcal{N}(0, g_{0}^2).               
\end{align}               
$$

Throughout we fix the variance of the network coefficient terms to match that of the intercept and elicit our priors for the average value of the networks, assuming they have been standardised. As a result, we can ignore the network matricies for elicitation.

### Prob of non-zero

We elicit the prior for $\eta_2$ based on the implied prior for $w_{ij}$, the probability that any element is non-zero. We want the implied prior on $w_{ij}$ to be $\textrm{Beta}\left(\frac{2}{p-1} \times 1, \frac{p - 3}{p-1}\times 1\right)$. 

Now we want to elicit a Gaussian on $\eta_2$ that will match this beta-distribution on $w$ as closely as possible. We can do this so as to match the mean and variance of the resulting prior for $w$, given the Gaussian prior on $\eta_2$ to that of the desires beta distribution. 

The mean and variance of a $w \sim \textrm{Beta}\left(\mu v, (1 - \mu)v\right)$ are
$$
\begin{align}
  \mathbb{E}[w] &= \mu\\
  \textrm{Var}[w]& = \frac{\mu(1-\mu)v^2}{(\mu v + (1-mu)v)^2(\mu v + (1-\mu)v + 1)}\\
  &= \frac{\mu(1-\mu)v^2}{v^2(v + 1)}\\
  &= \frac{\mu(1-\mu)}{(v + 1)}\\
\end{align}
$$

```{r GLASSO_SS_eta_2_prior_elicit_functions, include=TRUE,echo=TRUE, eval=TRUE,cache=TRUE}

var_beta_fn <- function(mu, v){
  return(mu*(1-mu)/(v + 1))
}

w_dist_SS <- function(m_02, s_02, N_MC){
  eta_2 <- rnorm(N_MC, m_02, s_02)
  w <- 1/(1+exp(-eta_2))
  return(w)
}

w_dist_SS_summaries <- function(m_02, s_02, N_MC){
  eta_2 <- rnorm(N_MC, m_02, s_02)
  w <- 1/(1+exp(-eta_2))
  return(list("mean" = mean(w), "var" = var(w)))
}

```

Then we can grid search over values of $m_2$ and $g_2$ whose Gaussian distribution matches the required Beta distribution

```{r GLASSO_SS_eta_2_prior_elicit_full, include=TRUE,echo=TRUE, eval=TRUE,cache=TRUE}

m2_seq <- seq(-3, -0.5, length.out = 10)
g2_seq <- seq(1.5, 3.5, length.out = 10)
mean_w <- array(NA, dim = c(length(m2_seq), length(g2_seq)))
var_w <- array(NA, dim = c(length(m2_seq), length(g2_seq)))

for(j in 1:length(m2_seq)){
  for(k in 1:length(g2_seq)){
    eval_temp <- w_dist_SS_summaries(m_02 = m2_seq[j], s_02 = g2_seq[k], N_MC = 5000)
    mean_w[j, k] <- eval_temp$mean
    var_w[j, k] <- eval_temp$var
    cat("m0", m2_seq[j], ", s0 ", g2_seq[k], "done", "\n")
  }
}

```

### Lower bounding the slab variance 

+ We want the mode of the slab to be one orders of magnitude greater than the spike
+ Then we can further say that we want the slab to be at the very least 3 times greater than that of the spike, with very very high probability (e.g. 0.99)


```{r GLASSO_SS_eta_1_prior_elict_functions, include=TRUE,echo=TRUE, eval=TRUE,cache=TRUE}

s1_dist_SS <- function(s0, m_01, s_01, N_MC){
  eta_1 <- rnorm(N_MC, m_01, s_01)
  s1 <- s0*(1+exp(-eta_1))
  return(s1)
}

s1_dist_SS_summaries <- function(s0, m_01, s_01, N_MC, lower_thresh){
  eta_1 <- rnorm(N_MC, m_01, s_01)
  s1 <- s0*(1+exp(-eta_1))
  return(list("mode_multiplier" = (1+exp(-m_01)), "lower_multiplier" = mean(as.numeric(s1 >= lower_thresh*s0))))
}


```

I could elicit the location via the mode, and the variance by a grid search for the 0.99 probability 

```{r GLASSO_SS_eta_1_prior_elict, include=TRUE,echo=TRUE, eval=TRUE,cache=TRUE}

#spike_scale_mode_multiplier <- 100
spike_scale_mode_multiplier <- 10
m_01_set_GLASSO_SS <- -log(spike_scale_mode_multiplier - 1)
m_01_set_GLASSO_SS


#spike_scale_lower_multiplier <- 10
spike_scale_lower_multiplier <- 5

m1_seq <- array(m_01_set_GLASSO_SS, dim = c(1))
g1_seq <- seq(0.5, 2, length.out = 20)
mode_s1 <- array(NA, dim = c(length(m1_seq), length(g1_seq)))
lower_prob <- array(NA, dim = c(length(m1_seq), length(g1_seq)))

for(j in 1:length(m1_seq)){
  for(k in 1:length(g1_seq)){
    eval_temp <- s1_dist_SS_summaries(s0 = spike_scale_set, m_01 = m1_seq[j], s_01 = g1_seq[k], N_MC = 5000, lower_thresh = spike_scale_lower_multiplier)
    mode_s1[j, k] <- eval_temp$mode_multiplier
    lower_prob[j, k] <- eval_temp$lower_multiplier
    cat("m1", m1_seq[j], ", g1 ", g1_seq[k], "done", "\n")
  }
}

```

### Being Positive Definite 

Above we have been able to elicit the priors for $\eta_2$ based on sparisty/uninformity and $\eta_1$ based on non-degeneracy (to the spike). Given everything else maybe we can elicit the variances of the eta_0's to be as big as possible whilst maintaining PD


```{r priorExpected_GLASSO_SS_PD_functions, include=TRUE,echo=TRUE, eval=TRUE,cache=TRUE}

dlaplace_SS <- function(rho, s0, eta_0, eta_1, eta_2){
  w <- 1/(1+ exp(-eta_2))
  s1 <- s0*(1+exp(-eta_1))
  return((1-w)*dlaplace(rho, 0, s0) + w*dlaplace(rho, eta_0, s1))
  }

# Laplace spike-and-slab generation
rSSLapalce <- function(n, s0, eta_0, eta_1, eta_2){
  w <- 1/(1 + exp(-eta_2))
  slab <- sample(c(0, 1), n, replace = TRUE, prob = c(1-w, w))
  s1 <- s0*(1+exp(-eta_1))
  return((1-slab)*rlaplace(n, 0, s0) + slab*rlaplace(n, eta_0, s1))
}

priorExp_GLASSO_SS_PD_matrix_prob <- function(p, s0, eta_0_p, eta_1_p, eta_2_p, N_MC, verbose = FALSE){
  # p is the dimension of the matrix 
  # eta_j_p are the parameters of the Gaussian distribution on the parameters of the Spike-and-Slab distributions
  # N_MC is the number of repeats wanted to provide the estimate of PD
  
  corr_mat_ind <- rep(NA, N_MC)
  for(j in 1:N_MC){
      eta_0 <- rnorm(1, eta_0_p[1], eta_0_p[2])
      eta_1 <- rnorm(1, eta_1_p[1], eta_1_p[2])
      eta_2 <- rnorm(1, eta_2_p[1], eta_2_p[2])
      corr_mat_values <- rSSLapalce(p*(p-1)/2, s0, eta_0, eta_1, eta_2)
      corr_mat <- corrType_mat_fill(p, values = corr_mat_values)
      corr_mat_ind[j] <- is.corrMat(corr_mat)
      if(verbose == TRUE){
        if((j %% (N_MC/10)) == 1){
          cat(j/N_MC * 100, "% done", "\n")
        }
      }
  }
  return(list("prob_PD" = mean(corr_mat_ind)))
}


```

```{r GLASSO_SS_eta_0_prior_elicit, include=TRUE,echo=TRUE, eval=TRUE,cache=TRUE}
#p <- 5
p <- 10

m_00_set_GLASSO_SS <- 0


g0_seq <- seq(0.001, 0.5, length.out = 20)
prob_PD <- rep(NA, length(g0_seq))

for(j in 1:length(g0_seq)){
  eval_temp <- priorExp_GLASSO_SS_PD_matrix_prob(p, spike_scale_set, eta_0_p = c(m_00_set_GLASSO_SS, g0_seq[j]), eta_1_p = c(m_01_set_GLASSO_SS, s_01_set_GLASSO_SS), eta_2_p = c(m_02_set_GLASSO_SS, s_02_set_GLASSO_SS), N_MC = 5000, verbose = FALSE)
  prob_PD[j] <- eval_temp$prob_PD
  cat("g0 ", g0_seq[j], "done", "\n")
}

```

```{r GLASSO_SS_eta_0_prior_elicit_plot, include=TRUE,echo=TRUE, eval=TRUE,cache=FALSE}

plot(g0_seq, prob_PD, xlab = "s_00", ylab = "Probability of PD", type = "l", lwd = 3, main = paste("p = ", p))

```


```{r GLASSO_SS_eta_0_prior_elicit_full_set, include=TRUE,echo=TRUE, eval=TRUE,cache=TRUE}

target_prob <- 0.95

s_00_set_GLASSO_SS <- g0_seq[which.min(abs(prob_PD - target_prob))]
s_00_set_GLASSO_SS

prob_PD[which(g0_seq == s_00_set_GLASSO_SS)]

```


### Plotting draws from the prior predictive


```{r GLASSO_SS_prior predictive_functions, include=TRUE,echo=TRUE, eval=TRUE,cache=TRUE}

GLASSO_SS_prior_predictive_sample <- function(n, s0, eta_0_p, eta_1_p, eta_2_p){
  # p is the dimension of the matrix 
  # eta_j_p are the parameters of the Gaussian distribution on the parameters of the Spike-and-Slab distributions
  # N_MC is the number of repeats wanted to provide the estimate of PD
  
  eta_0 <- rnorm(n, eta_0_p[1], eta_0_p[2])
  eta_1 <- rnorm(n, eta_1_p[1], eta_1_p[2])
  eta_2 <- rnorm(n, eta_2_p[1], eta_2_p[2])
  #rho <- rSSLapalce(n, s0, eta_0, eta_1, eta_2) ## sample can't handle vector valued w
  rho <- rep(NA, n)
  for(j in 1:n){
    rho[j] <- rSSLapalce(1, s0, eta_0[j], eta_1[j], eta_2[j])
  }
  
  return(rho)
}

samp_test <- GLASSO_SS_prior_predictive_sample(n = 5000, spike_scale_set, eta_0_p = c(m_00_set_GLASSO_SS, s_00_set_GLASSO_SS), eta_1_p = c(m_01_set_GLASSO_SS, s_01_set_GLASSO_SS), eta_2_p = c(m_02_set_GLASSO_SS, s_02_set_GLASSO_SS))

hist(samp_test, breaks = 20)
      
      
```

## GLASSO-SS

```{r GLASSO_SS_prior_elicit_function, include=TRUE,echo=TRUE, eval=TRUE,cache=TRUE}

GLASSO_SS_prior_elicit <- function(p, g0_seq, m1_seq = NULL, g1_seq, m2_seq, g2_seq, prob_PD_thresh, spike_scale_mode_multiplier, spike_scale_lower_multiplier, target_mean_w = 1*2/(p-1), target_var_w, thresh = 0.01, N_MC = 5000, verbose = FALSE){
  
  prob_thresh <- 0.95
  spike_scale_optim <- optimize(f = function(s0){abs((plaplace(thresh, 0, s0) - plaplace(-thresh, 0, s0)) - prob_thresh)}, lower = 0, upper = 1)

  spike_scale_set <- spike_scale_optim$minimum

  ## eta2
  mean_w <- array(NA, dim = c(length(m2_seq), length(g2_seq)))
  var_w <- array(NA, dim = c(length(m2_seq), length(g2_seq)))

  for(j in 1:length(m2_seq)){
    for(k in 1:length(g2_seq)){
      eval_temp <- w_dist_SS_summaries(m_02 = m2_seq[j], s_02 = g2_seq[k], N_MC)
      mean_w[j, k] <- eval_temp$mean
      var_w[j, k] <- eval_temp$var
      if(verbose == TRUE){
        cat("eta2: m0", m2_seq[j], ", s0 ", g2_seq[k], "done", "\n")
      }
    }
  }
  
  min_obj <- min(abs(mean_w - target_mean_w) + abs(var_w - target_var_w))

  ind_set <- which((abs(mean_w - target_mean_w) + abs(var_w - target_var_w)) == min_obj, arr.ind = TRUE)

  m_02_set_GLASSO_SS <- m2_seq[ind_set[1]]
  s_02_set_GLASSO_SS <- g2_seq[ind_set[2]]

  elicited_mean_w <- mean_w[ind_set[1], ind_set[2]]
  elicited_var_w <- var_w[ind_set[1], ind_set[2]]
  
  ## eta1
  if(is.null(m1_seq) == TRUE){
    m_01_set_GLASSO_SS <- -log(spike_scale_mode_multiplier - 1)
    m1_seq <- array(m_01_set_GLASSO_SS, dim = c(1))
  }
  
  mode_s1 <- array(NA, dim = c(length(m1_seq), length(g1_seq)))
  lower_prob <- array(NA, dim = c(length(m1_seq), length(g1_seq)))

  for(j in 1:length(m1_seq)){
    for(k in 1:length(g1_seq)){
      eval_temp <- s1_dist_SS_summaries(s0 = spike_scale_set, m_01 = m1_seq[j], s_01 = g1_seq[k], N_MC, lower_thresh = spike_scale_lower_multiplier)
      mode_s1[j, k] <- eval_temp$mode_multiplier
      lower_prob[j, k] <- eval_temp$lower_multiplier
      if(verbose == TRUE){
        cat("eta1: m1", m1_seq[j], ", g1 ", g1_seq[k], "done", "\n")
      }
      }
  }
  
  target_mode <- spike_scale_mode_multiplier
  target_lower_prob <- 0.99

  min_obj <- min(abs(mode_s1 - target_mode) + abs(lower_prob - target_lower_prob))

  ind_set <- which((abs(mode_s1 - target_mode) + abs(lower_prob - target_lower_prob)) == min_obj, arr.ind = TRUE)

  #m_01_set_GLASSO_SS <- m1_seq[ind_set[1]]
  s_01_set_GLASSO_SS <- g1_seq[ind_set[2]]
  
  elicited_mode_multiplier <- mode_s1[ind_set[1], ind_set[2]]
  elicited_lower_multiplier <- lower_prob[ind_set[1], ind_set[2]]
  
  ## eta0
  m_00_set_GLASSO_SS <- 0

  prob_PD <- rep(NA, length(g0_seq))
  for(j in 1:length(g0_seq)){
    eval_temp <- priorExp_GLASSO_SS_PD_matrix_prob(p, spike_scale_set, eta_0_p = c(m_00_set_GLASSO_SS, g0_seq[j]), eta_1_p = c(m_01_set_GLASSO_SS, s_01_set_GLASSO_SS), eta_2_p = c(m_02_set_GLASSO_SS, s_02_set_GLASSO_SS), N_MC, verbose = FALSE)
    prob_PD[j] <- eval_temp$prob_PD
    if(verbose == TRUE){
      cat("eta0: g0 ", g0_seq[j], "done", "\n")
    }
}

  s_00_set_GLASSO_SS <- g0_seq[which.min(abs(prob_PD - prob_PD_thresh))]

  elicited_prob_PD <- prob_PD[which(g0_seq == s_00_set_GLASSO_SS)]
  
  return(list(
    "prior_params" = list("spike_scale" = spike_scale_set, "m_00" = m_00_set_GLASSO_SS, "s_00" = s_00_set_GLASSO_SS, "m_01" = m_01_set_GLASSO_SS, "s_01" = s_01_set_GLASSO_SS, "m_02" = m_02_set_GLASSO_SS, "s_02" = s_02_set_GLASSO_SS),
    "elicitation_criteria" = list("spike_density_error" = spike_scale_optim$objective, "Prob_PD" = elicited_prob_PD, "mode_multiplier" =   elicited_mode_multiplier, "lower_multiplier" = elicited_lower_multiplier, "mean_w" = elicited_mean_w, "var_w" = elicited_var_w)
  ))

  
}

```

# p = 10 {.tabset}

## GLASSO Spike-and-Slab

```{r GLASSO_SS_p10_prior_elicit_function_run, include=TRUE,echo=TRUE, eval=TRUE,cache=TRUE}
p <- 10

# This is a univarite optimisation so could make this longer
g0_seq <- seq(0.0001, 0.2, length.out = 30)

g1_seq <- seq(0.05, 1.5, length.out = 20)

m2_seq <- seq(-3, -0.5, length.out = 10)
g2_seq <- seq(1.5, 3.5, length.out = 10)


target_mean_w <- 2/(p-1)
target_mean_w
target_var_w <- var_beta_fn(mu = target_mean_w, v = 1)
target_var_w

#spike_scale_mode_multiplier <- 30
spike_scale_mode_multiplier <- 10
#spike_scale_lower_multiplier <- 10
spike_scale_lower_multiplier <- 3

target_mode_s1 <- spike_scale_mode_multiplier
target_mode_s1
target_lower_prob_s1 <- 0.99

prob_PD_thresh <- 0.95

GLASSO_SS_p10_prior_params <- GLASSO_SS_prior_elicit(p, g0_seq, m1_seq = NULL, g1_seq, m2_seq, g2_seq, prob_PD_thresh, spike_scale_mode_multiplier, spike_scale_lower_multiplier, target_mean_w, target_var_w, thresh, N_MC = 5000, verbose = FALSE)


```

```{r GLASSO_SS_p10_prior_elicit_function_run_diag, include=TRUE,echo=TRUE, eval=TRUE,cache=FALSE}

GLASSO_SS_p10_prior_params$prior_params
GLASSO_SS_p10_prior_params$elicitation_criteria

```

### Samples from the prior predictive

```{r GLASSO_SS_p10_prior_elicit_plot, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE, fig.height = 3, fig.width = 5}

par(mar = c(3.1, 3.3, 1.5, 1.1))  # bottom, left, top, right
#par(mar = c(5.1, 4.1, 4.1, 2.1)) # Default
#par(mgp = c(3, 1, 0)) # Default  - location of xlab and ylab, tick-mark labels, tick marks.
par(mgp = c(2.15, 1, 0))
par(cex.lab = 1.25, cex.axis = 1.25, cex.main = 1.25)

GLASSO_SS_p10_samp <- GLASSO_SS_prior_predictive_sample(n = 5000, s0 = spike_scale_set, 
                      eta_0_p = c(GLASSO_SS_p10_prior_params$prior_params$m_00, GLASSO_SS_p10_prior_params$prior_params$s_00), 
                      eta_1_p = c(GLASSO_SS_p10_prior_params$prior_params$m_01, GLASSO_SS_p10_prior_params$prior_params$s_01), 
                      eta_2_p = c(GLASSO_SS_p10_prior_params$prior_params$m_02, GLASSO_SS_p10_prior_params$prior_params$s_02))

hist(GLASSO_SS_p10_samp, breaks = 100, xlim = c(-1, 1), probability = TRUE, ylab = "Density", xlab = "rho", main = "p = 10", ylim = c(0, 5), xaxs = "i")#, yaxs = "i")
box()
  
```


# p = 50 {.tabset}

## GLASSO Spike-and-Slab

Be careful not to elict s_00 too small

```{r GLASSO_SS_p50_prior_elicit_function_run, include=TRUE,echo=TRUE, eval=TRUE,cache=TRUE}
p <- 50

# This is a univarite optimisation so could make this longer
g0_seq <- seq(0.0001, 0.2, length.out = 30)

g1_seq <- seq(0.05, 1.5, length.out = 20)

#m2_seq <- seq(-4, -0.5, length.out = 10)
m2_seq <- seq(-8, -2, length.out = 20)
g2_seq <- seq(0.5, 5.5, length.out = 20)


target_mean_w <- 2/(p-1)
target_mean_w
target_var_w <- var_beta_fn(mu = target_mean_w, v = 1)
target_var_w

#spike_scale_mode_multiplier <- 30
spike_scale_mode_multiplier <- 10
#spike_scale_lower_multiplier <- 10
spike_scale_lower_multiplier <- 3

target_mode_s1 <- spike_scale_mode_multiplier
target_mode_s1
target_lower_prob_s1 <- 0.99

prob_PD_thresh <- 0.95

GLASSO_SS_p50_prior_params <- GLASSO_SS_prior_elicit(p, g0_seq, m1_seq = NULL, g1_seq, m2_seq, g2_seq, prob_PD_thresh, spike_scale_mode_multiplier, spike_scale_lower_multiplier, target_mean_w, target_var_w, thresh, N_MC = 5000, verbose = FALSE)


```

```{r GLASSO_SS_p50_prior_elicit_function_run_diag, include=TRUE,echo=TRUE, eval=TRUE,cache=FALSE}

GLASSO_SS_p50_prior_params$prior_params
GLASSO_SS_p50_prior_params$elicitation_criteria

```

### Samples from the prior predictive

```{r GLASSO_SS_p50_prior_elicit_plot, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE, fig.height = 3, fig.width = 5}

par(mar = c(3.1, 3.3, 1.5, 1.1))  # bottom, left, top, right
#par(mar = c(5.1, 4.1, 4.1, 2.1)) # Default
#par(mgp = c(3, 1, 0)) # Default  - location of xlab and ylab, tick-mark labels, tick marks.
par(mgp = c(2.15, 1, 0))
par(cex.lab = 1.25, cex.axis = 1.25, cex.main = 1.25)

GLASSO_SS_p50_samp <- GLASSO_SS_prior_predictive_sample(n = 5000, s0 = spike_scale_set, 
                      eta_0_p = c(GLASSO_SS_p50_prior_params$prior_params$m_00, GLASSO_SS_p50_prior_params$prior_params$s_00), 
                      eta_1_p = c(GLASSO_SS_p50_prior_params$prior_params$m_01, GLASSO_SS_p50_prior_params$prior_params$s_01), 
                      eta_2_p = c(GLASSO_SS_p50_prior_params$prior_params$m_02, GLASSO_SS_p50_prior_params$prior_params$s_02))

hist(GLASSO_SS_p50_samp, breaks = 100, xlim = c(-1, 1), probability = TRUE, ylab = "Density", xlab = "rho", main = "p = 10", ylim = c(0, 5), xaxs = "i")#, yaxs = "i")
box()
  
```


# COVID Data {.tabset}

## GLASSO Spike-and-Slab

```{r GLASSO_SS_COVID_prior_elicit_function_run, include=TRUE,echo=TRUE, eval=TRUE,cache=TRUE}

p <- 99

# This is a univarite optimisation so could make this longer
g0_seq <- seq(0.01, 0.15, length.out = 30)

g1_seq <- seq(0.05, 1.5, length.out = 20)

#m2_seq <- seq(-4, -0.5, length.out = 10)
#m2_seq <- seq(-8, -2, length.out = 20)
m2_seq <- seq(-10, -6, length.out = 20)
g2_seq <- seq(0.5, 5.5, length.out = 20)


target_mean_w <- 2/(p-1)
target_mean_w
target_var_w <- var_beta_fn(mu = target_mean_w, v = 1)
target_var_w

#spike_scale_mode_multiplier <- 30
spike_scale_mode_multiplier <- 10
#spike_scale_lower_multiplier <- 10
spike_scale_lower_multiplier <- 3

target_mode_s1 <- spike_scale_mode_multiplier
target_mode_s1
target_lower_prob_s1 <- 0.99

prob_PD_thresh <- 0.95

GLASSO_SS_COVID_prior_params <- GLASSO_SS_prior_elicit(p, g0_seq, m1_seq = NULL, g1_seq, m2_seq, g2_seq, prob_PD_thresh, spike_scale_mode_multiplier, spike_scale_lower_multiplier, target_mean_w, target_var_w, thresh, N_MC = 5000, verbose = FALSE)


```

```{r GLASSO_SS_COVID_prior_elicit_function_run_diag, include=TRUE,echo=TRUE, eval=TRUE,cache=FALSE}

p

GLASSO_SS_COVID_prior_params$prior_params
GLASSO_SS_COVID_prior_params$elicitation_criteria

```

### Samples from the prior predictive

```{r GLASSO_SS_COVID_prior_elicit_plot, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE, fig.height = 3, fig.width = 5}

par(mar = c(3.1, 3.3, 1.5, 1.1))  # bottom, left, top, right
#par(mar = c(5.1, 4.1, 4.1, 2.1)) # Default
#par(mgp = c(3, 1, 0)) # Default  - location of xlab and ylab, tick-mark labels, tick marks.
par(mgp = c(2.15, 1, 0))
par(cex.lab = 1.25, cex.axis = 1.25, cex.main = 1.25)

GLASSO_SS_COVID_samp <- GLASSO_SS_prior_predictive_sample(n = 5000, s0 = spike_scale_set, 
                      eta_0_p = c(GLASSO_SS_COVID_prior_params$prior_params$m_00, GLASSO_SS_COVID_prior_params$prior_params$s_00), 
                      eta_1_p = c(GLASSO_SS_COVID_prior_params$prior_params$m_01, GLASSO_SS_COVID_prior_params$prior_params$s_01), 
                      eta_2_p = c(GLASSO_SS_COVID_prior_params$prior_params$m_02, GLASSO_SS_COVID_prior_params$prior_params$s_02))

hist(GLASSO_SS_COVID_samp, breaks = 100, xlim = c(-1, 1), probability = TRUE, ylab = "Density", xlab = "rho", main = "COVID Data, p = 99", ylim = c(0, 5), xaxs = "i")#, yaxs = "i")
box()
  
```

# Stock Market Data {.tabset}

## GLASSO Spike-and-Slab

```{r GLASSO_SS_STOCK_prior_elicit_function_run, include=TRUE,echo=TRUE, eval=TRUE,cache=TRUE}

p <- 200

# This is a univarite optimisation so could make this longer
g0_seq <- seq(0.01, 0.15, length.out = 30)

g1_seq <- seq(0.05, 1.5, length.out = 20)

#m2_seq <- seq(-4, -0.5, length.out = 10)
#m2_seq <- seq(-8, -2, length.out = 20)
m2_seq <- seq(-10, -6, length.out = 20)
g2_seq <- seq(0.5, 5.5, length.out = 20)


target_mean_w <- 2/(p-1)
target_mean_w
target_var_w <- var_beta_fn(mu = target_mean_w, v = 1)
target_var_w

#spike_scale_mode_multiplier <- 30
spike_scale_mode_multiplier <- 10
#spike_scale_lower_multiplier <- 10
spike_scale_lower_multiplier <- 3

target_mode_s1 <- spike_scale_mode_multiplier
target_mode_s1
target_lower_prob_s1 <- 0.99

prob_PD_thresh <- 0.95

GLASSO_SS_STOCK_prior_params <- GLASSO_SS_prior_elicit(p, g0_seq, m1_seq = NULL, g1_seq, m2_seq, g2_seq, prob_PD_thresh, spike_scale_mode_multiplier, spike_scale_lower_multiplier, target_mean_w, target_var_w, thresh, N_MC = 5000, verbose = FALSE)


```

```{r GLASSO_SS_STOCK_prior_elicit_function_run_diag, include=TRUE,echo=TRUE, eval=TRUE,cache=FALSE}

GLASSO_SS_STOCK_prior_params$prior_params
GLASSO_SS_STOCK_prior_params$elicitation_criteria

```

### Samples from the prior predictive

```{r GLASSO_SS_STOCK_prior_elicit_plot, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE, fig.height = 3, fig.width = 5}

par(mar = c(3.1, 3.3, 1.5, 1.1))  # bottom, left, top, right
#par(mar = c(5.1, 4.1, 4.1, 2.1)) # Default
#par(mgp = c(3, 1, 0)) # Default  - location of xlab and ylab, tick-mark labels, tick marks.
par(mgp = c(2.15, 1, 0))
par(cex.lab = 1.25, cex.axis = 1.25, cex.main = 1.25)

GLASSO_SS_STOCK_samp <- GLASSO_SS_prior_predictive_sample(n = 5000, s0 = spike_scale_set, 
                      eta_0_p = c(GLASSO_SS_STOCK_prior_params$prior_params$m_00, GLASSO_SS_STOCK_prior_params$prior_params$s_00), 
                      eta_1_p = c(GLASSO_SS_STOCK_prior_params$prior_params$m_01, GLASSO_SS_STOCK_prior_params$prior_params$s_01), 
                      eta_2_p = c(GLASSO_SS_STOCK_prior_params$prior_params$m_02, GLASSO_SS_STOCK_prior_params$prior_params$s_02))

hist(GLASSO_SS_STOCK_samp, breaks = 100, xlim = c(-1, 1), probability = TRUE, ylab = "Density", xlab = "rho", main = "p = 10", ylim = c(0, 5), xaxs = "i")#, yaxs = "i")
box()
  
```

