---
title: "COVID Network GLASSO out-of-sample Analysis - 10-fold cross-validation"
author: "Jack Jewson"
date: "19/07/2022"
output: html_document
---

Here we run the Network GLASSO for the COVID19 data using the Geodist and Facebook networks

# Preliminaries {.tabset}

## working directory

```{r working_directory, include=TRUE,echo=TRUE, eval=TRUE,cache=FALSE}

data_dir <- '/home/usuario/Documents/Barcelona_Yr1/GraphicalModels_NetworkData/LiLicode/paper_code_github/'

```

## Packages

```{r packages, include=TRUE,echo=TRUE, eval=TRUE,cache=FALSE}
library(readr)
library(devtools)
#install_github("pzwiernik/golazo", build_vignettes=TRUE)
library(golazo)
#source('Network_GLASSO/GOLAZO_function.R')
library(polynom)
library(ggplot2)

library(graphics)
library(mvtnorm)
library(xtable)
library(knitr)
```

### Parallel Cross-Validation

```{r packages_cv, include=TRUE,echo=TRUE, eval=TRUE,cache=FALSE}
library(foreach)
library(doParallel)

#setup parallel backend to use many processors
#cores=detectCores() - 
#cores <- cores[1] - 1 #not to overload your computer
cores <- 5
cl <- makeCluster(cores) 
registerDoParallel(cl)

```

## Functions 

```{r functions, include=TRUE,echo=TRUE, eval=TRUE,cache=TRUE}

ebic_eval <- function(n, R, U, ebic.gamma, edge.tol){
  res <- golazo(R, L = -U, U = U, verbose = FALSE)
  K <- res$K
  KR <- stats::cov2cor(K)         #to make edge count independend of scalings
  nedg <- length(which(abs(KR[upper.tri(abs(KR), diag = FALSE)]) > edge.tol))
  ## p is the dimensions of R I think - this should be fine but isn't great code!
  ebic <- -(n)*(log(det(K)) - sum(R*K)) + nedg * (log(n) + 4 * ebic.gamma * log(p))
  return(ebic)   
}

ebic_eval_network <- function(n, R, A, beta0, beta1, ebic.gamma, edge.tol){
  U <- exp(beta0 + beta1*A) 
  diag(U) <- 0
  return(ebic_eval(n, R, U, ebic.gamma, edge.tol))
}

ebic_eval_two_networks <- function(n, R, A1, A2, beta0, beta1, beta2, ebic.gamma, edge.tol){
   U <- exp(beta0 + beta1*A1 + beta2*A2) 
   diag(U) <- 0
   return(ebic_eval(n, R, U, ebic.gamma, edge.tol))
}


standardise_network_matrix_tri <- function(A) {
  p <- nrow(A)
  
  A_tri <- A[upper.tri(A)]
  bar_A_tri <- mean(A_tri)
  S2_A_tri <- 1/length(A_tri)*sum((A_tri - bar_A_tri)^2)
  
  return((A - bar_A_tri)/sqrt(S2_A_tri))
}

## Turning the correlation matrix given by the golazo function back to a covariance matrix, useful in out-of-sample-llh
cor2cov <- function(Theta_cor, sigma2_vect){
  # Theta_cor is correlation matrix, sqrt(sigma2_vect) is the standard deviations of each variable
  p <- nrow(Theta_cor)
  Theta_cov <- matrix(NA, nrow = p, ncol = p)
  for(i in 1:p){
    Theta_cov[, i] <- Theta_cor[,i]*sqrt(sigma2_vect[i])*sqrt(sigma2_vect)   
  }
  return(Theta_cov)
}


threshold <- function(Rho_mat, threshold){
  return(Rho_mat*(abs(Rho_mat) >= threshold))
}



## No Network matrix
beta0_max_GLASSO <- function(R){
  return(log(max(abs(R - diag(diag(R))))))## check we can irgnore diags
}


```

## Hyparameters

```{r hyperparameters, include=TRUE,echo=TRUE, eval=TRUE,cache=TRUE}

ebic.gamma <- 0           # set to zero to get BIC
edge.tol <-  1e-6         # be consistent with GLASSO+EBIC method

```

# Data Loading

```{r data_load, include=TRUE,echo=TRUE, eval=TRUE,cache=TRUE}

setwd(data_dir)

covid1 <- as.matrix(read_csv("Data/COVID/Pre-processed Data/covid1.csv"))[,2:100]

geodist1 <- as.matrix(read_csv("Data/COVID/Pre-processed Data/geodist1.csv"))[,2:100]
SCI_index1 <- as.matrix(read_csv("Data/COVID/Pre-processed Data/SCI_index1.csv"))[,2:100]

n <- nrow(covid1)
p <- ncol(covid1)
N <- 1

```

# Training and Testing

```{r training_testing, include=TRUE,echo=TRUE, eval=TRUE,cache=TRUE}

N_folds <- 10

n <- round(nrow(covid1)/N_folds)

train_data <- list()
test_data <- list()

set.seed(1234)
covid_seq_shuffle <- sample(seq_len(nrow(covid1)), nrow(covid1), replace = FALSE)

for (i in 1:(N_folds - 1)){
  picked <- (i - 1)*n + 1:n 
  train_data[[i]] <- covid1[-covid_seq_shuffle[picked], ]
  test_data[[i]]  <- covid1[covid_seq_shuffle[picked], ]
}
not_picked <- 1:((N_folds - 1)*n) 
train_data[[N_folds]] <- covid1[covid_seq_shuffle[not_picked], ]
test_data[[N_folds]]  <- covid1[-covid_seq_shuffle[not_picked], ]
  
  
N <- N_folds  
```

Need to standardise to test set to score per observation to combine

# GLASSO {.tabset}

## Inference

```{r GLASSO_run, include=TRUE,echo=TRUE, eval=TRUE,cache=TRUE}

L <- matrix(-1,p,p)    
U <- matrix (1,p,p)
diag(U) <- diag(L) <- 0

beta0_GLASSO <-rep(NA, N)
#beta0_grid_length <- 20
#beta0_grid_min <- -3
beta0_grid_max <- rep(-1, N)
beta0_grid_min <- rep(-2.5, N)

GLASSO_sim_results <- foreach(j=1:N, .combine = 'rbind',.packages = c("stats", "golazo", "mvtnorm")) %dopar% {

  n <- nrow(train_data[[j]])
  
  #### Estimating lambda ####
  R <- stats::cov2cor(cov(train_data[[j]]))  
  
  ## grid-search ##
  #beta0_grid_max <- beta0_max_GLASSO(R)
  #beta0_grid <- seq(beta0_grid_min, beta0_grid_max, length.out = beta0_grid_length )
  
  beta0_grid <- seq(beta0_grid_min[j], beta0_grid_max[j], length.out = beta0_grid_length)
  
  beta_optimise <- rep(NA, beta0_grid_length)
  
  for(b in 1:beta0_grid_length){
    #cat("b = ", b, "\n")
    beta_optimise[b] <- ebic_eval(n, R, U = exp(beta0_grid[b])*U, ebic.gamma, edge.tol = edge.tol)
  }
  
  beta0_GLASSO <- beta0_grid[which.min(beta_optimise)]

  ebic_eval_optim_GLASSO <- min(beta_optimise)
  
  #### Using the optimal beta0 ##
  GraphicalModel <- golazo (R, L = exp(beta0_GLASSO) * L, U =exp(beta0_GLASSO)* U, tol = 1e-7, verbose=FALSE)
  
  Theta_hat_GLASSO <- threshold(GraphicalModel$K, edge.tol)  
  Rho_hat_GLASSO <- threshold(cov2cor(GraphicalModel$K), edge.tol)
  
  #out-of-sample log-likelihood
  n_test <- nrow(test_data[[j]])
  
  out_sample_llh_GLASSO <- 1/n_test*sum(dmvnorm(test_data[[j]], mean = rep(0, p), sigma = cor2cov(cov2cor(solve(Rho_hat_GLASSO)), diag(cov(train_data[[j]]))), log = TRUE))
  
  c(beta0_GLASSO, ebic_eval_optim_GLASSO, out_sample_llh_GLASSO)

}

```

## Analysis

```{r GLASSO_diag, include=TRUE,echo=TRUE, eval=TRUE,cache=FALSE}

GLASSO_sim_results

mean(GLASSO_sim_results[,2])
mean(GLASSO_sim_results[,3])

```

# Networks {.tabset}

## Geodist (A1)

```{r Theta_vs_A1, include=TRUE,echo=TRUE, eval=TRUE,cache=TRUE}

A1 <- as.matrix(geodist1)
A1 <- 1/log(A1) 
A1 <- standardise_network_matrix_tri(A1)
diag(A1) <- 0

```

## Facebook (A2)

```{r Theta_vs_A2, include=TRUE,echo=TRUE, eval=TRUE,cache=TRUE}

A2 <- as.matrix(SCI_index1)
A2 <- log(A2)
A2 <- standardise_network_matrix_tri(A2)
diag(A2) <- 0
```

# GOLAZO - Geodist (A1) {.tabset}

## Inference

```{r GOLAZO_A1, include=TRUE,echo=TRUE, eval=TRUE,cache=TRUE}

L <- matrix(-1,p,p)    
U <- matrix (1,p,p)
diag(U) <- diag(L) <- 0

beta_GOLAZO_A1_out <- matrix(NA, nrow = N, ncol = 2)

#beta0_grid_length <- 20
#beta0_grid_max <- 2
#beta0_grid_min <- -5

#beta0_grid <- seq(beta0_grid_min, beta0_grid_max, length.out = beta0_grid_length - 1)
#beta0_grid <- sort(c(beta0_grid, 0)) 

beta0_grid_length <- 20
beta0_grid_max <- c(1.25, 1.25, 0.75, 0.75, 0.5, 0.75, 0.75, 0.5, 0.75, 0.5)
beta0_grid_min <- c(-0.25, -0.25, -0.75, -0.75, -1, -0.75, -0.75, -1, -0.75, -1)

#beta1_grid_length <- 20
#beta1_grid_max <- 2
#beta1_grid_min <- -5

#beta1_grid <- seq(beta1_grid_min, beta1_grid_max, length.out = beta1_grid_length - 1)
#beta1_grid <- sort(c(beta1_grid, 0)) 

beta1_grid_length <- 20
beta1_grid_max <- c(-0.75, -0.75,-0.25, -0.75, -0.25, -0.75, -0.75, -0.25, -0.25, -0.25)
beta1_grid_min <- c(-2.25, -2.25,-1.75, -2.25, -1.75, -2.25, -2.25, -1.75, -1.75, -1.75)



GOLAZO_A1_sim_results <- foreach(j=1:N, .combine = 'rbind',.packages = c("stats", "golazo", "mvtnorm")) %dopar% {
  
  n <- nrow(train_data[[j]])
  
  #### Estimating lambda ####
  R <- stats::cov2cor(cov(train_data[[j]]))
  
  beta0_grid <- seq(beta0_grid_min[j], beta0_grid_max[j], length.out = beta0_grid_length)
  beta1_grid <- seq(beta1_grid_min[j], beta1_grid_max[j], length.out = beta1_grid_length)
  
  beta_optimise <- matrix(NA, nrow = beta0_grid_length, ncol = beta1_grid_length)
  for(b0 in 1:beta0_grid_length){
    for(b1 in 1:beta1_grid_length){
      #cat("b0 = ", b0, ", b1 = ", b1, "\n")
      try(beta_optimise[b0, b1] <- ebic_eval_network(n, R, A1, beta0 = beta0_grid[b0], beta1 = beta1_grid[b1], ebic.gamma, edge.tol), silent = TRUE)
    }
    #cat("b0 = ", b0, "DONE", "\n")
  }
  
  min_coord <- which(beta_optimise== min(beta_optimise, na.rm = TRUE), arr.ind = TRUE)
  
  beta_GOLAZO_A1_out[1] <- beta0_grid[min_coord[1]]
  beta_GOLAZO_A1_out[2] <- beta1_grid[min_coord[2]]
  ebic_eval_optim_GOLAZO_A1_out <- min(beta_optimise, na.rm = TRUE)
  
  # U <- exp(beta0 + beta1*A1) 
  U <- exp(beta_GOLAZO_A1_out[1] + beta_GOLAZO_A1_out[2]*A1) 
  
  ###################################
  # we are now ready to run GOLAZO and output the optimal K
  diag(U) <- 0
  
  res <- golazo(R, -U, U, tol = 1e-7, verbose=FALSE)
  Rho_hat_GOLAZO_A1_out <- threshold(cov2cor(res$K), edge.tol)
  
  #out-of-sample log-likelihood
  n_test <- nrow(test_data[[j]])
  
  out_sample_llh_GOLAZO_A1 <- 1/n_test*sum(dmvnorm(test_data[[j]], mean = rep(0, p), sigma = cor2cov(cov2cor(solve(Rho_hat_GOLAZO_A1_out)), diag(cov(train_data[[j]]))), log = TRUE))
  
  c(beta_GOLAZO_A1_out, ebic_eval_optim_GOLAZO_A1_out, out_sample_llh_GOLAZO_A1)
  
}
```

## Analysis

```{r GOLAZO_A1_diag, include=TRUE,echo=TRUE, eval=TRUE,cache=FALSE}

GOLAZO_A1_sim_results

mean(GOLAZO_A1_sim_results[,21])
mean(GOLAZO_A1_sim_results[,22])

```


# GOLAZO - Facebook (A2) {.tabset}

## Inference

```{r GOLAZO_A2, include=TRUE,echo=TRUE, eval=TRUE,cache=TRUE}

L <- matrix(-1,p,p)    
U <- matrix (1,p,p)
diag(U) <- diag(L) <- 0

beta_GOLAZO_A2_out <- matrix(NA, nrow = N, ncol = 2)

#beta0_grid_length <- 20
#beta0_grid_max <- 2
#beta0_grid_min <- -5

#beta0_grid <- seq(beta0_grid_min, beta0_grid_max, length.out = beta0_grid_length - 1)
#beta0_grid <- sort(c(beta0_grid, 0)) 

beta0_grid_length <- 20
beta0_grid_max <- c(1.25, 0.75, 1.25, 1.25, 0.75, 2, 0.5, 1.25, 1.25, 0.75)
beta0_grid_min <- c(-0.25, -0.75, -0.25, -0.25, -0.75, 0.5, -1, -0.25, -0.25, -0.75)

#beta2_grid_length <- 20
#beta2_grid_max <- 2
#beta2_grid_min <- -5

#beta2_grid <- seq(beta2_grid_min, beta2_grid_max, length.out = beta2_grid_length - 1)
#beta2_grid <- sort(c(beta2_grid, 0)) 

beta2_grid_length <- 20
beta2_grid_max <- c(-0.75, -0.75,-0.25, -0.75, -0.25, -0.75, -0.75, -0.25, -0.25, -0.25)
beta2_grid_min <- c(-2.25, -2.25,-1.75, -2.25, -1.75, -2.25, -2.25, -1.75, -1.75, -1.75)


GOLAZO_A2_sim_results <- foreach(j=1:N, .combine = 'rbind',.packages = c("stats", "golazo", "mvtnorm")) %dopar% {
  
  n <- nrow(train_data[[j]])
  
  #### Estimating lambda ####
  R <- stats::cov2cor(cov(train_data[[j]])) 
  
  beta0_grid <- seq(beta0_grid_min[j], beta0_grid_max[j], length.out = beta0_grid_length)
  beta2_grid <- seq(beta2_grid_min[j], beta2_grid_max[j], length.out = beta2_grid_length)
  
  beta_optimise <- matrix(NA, nrow = beta0_grid_length, ncol = beta2_grid_length)
  for(b0 in 1:beta0_grid_length){
    for(b1 in 1:beta2_grid_length){
      #cat("b0 = ", b0, ", b1 = ", b1, "\n")
      try(beta_optimise[b0, b1] <- ebic_eval_network(n, R, A2, beta0 = beta0_grid[b0], beta1 = beta2_grid[b1], ebic.gamma, edge.tol), silent = TRUE)
    }
    #cat("b0 = ", b0, "DONE", "\n")
  }
  
  min_coord <- which(beta_optimise== min(beta_optimise, na.rm = TRUE), arr.ind = TRUE)
  
  beta_GOLAZO_A2_out[1] <- beta0_grid[min_coord[1]]
  beta_GOLAZO_A2_out[2] <- beta2_grid[min_coord[2]]
  ebic_eval_optim_GOLAZO_A2_out <- min(beta_optimise, na.rm = TRUE)
  
  # U <- exp(beta0 + beta1*A2) 
  U <- exp(beta_GOLAZO_A2_out[1] + beta_GOLAZO_A2_out[2]*A2) 
  
  ###################################
  # we are now ready to run GOLAZO and output the optimal K
  diag(U) <- 0
  
  res <- golazo(R, -U, U, tol = 1e-7, verbose=FALSE)
  Rho_hat_GOLAZO_A2_out <- threshold(cov2cor(res$K), edge.tol)
  
  #out-of-sample log-likelihood
  n_test <- nrow(test_data[[j]])
  
  out_sample_llh_GOLAZO_A2 <- 1/n_test*sum(dmvnorm(test_data[[j]], mean = rep(0, p), sigma = cor2cov(cov2cor(solve(Rho_hat_GOLAZO_A2_out)), diag(cov(train_data[[j]]))), log = TRUE))
  
  c(beta_GOLAZO_A2_out, ebic_eval_optim_GOLAZO_A2_out, out_sample_llh_GOLAZO_A2)
  
}

```

## Analysis

```{r GOLAZO_A2_diag, include=TRUE,echo=TRUE, eval=TRUE,cache=FALSE}

GOLAZO_A2_sim_results

mean(GOLAZO_A2_sim_results[,21])
mean(GOLAZO_A2_sim_results[,22])

```

# GOLAZO - Geodist & Facebook (A1 & A2) {.tabset}

## Inference

```{r GOLAZO_A1A2, include=TRUE,echo=TRUE, eval=TRUE,cache=TRUE}

L <- matrix(-1,p,p)    
U <- matrix (1,p,p)
diag(U) <- diag(L) <- 0


beta_GOLAZO_A1A2_out <- matrix(NA, nrow = N, ncol = 3)

#beta0_grid_length <- 10
#beta0_grid_max <- 2
#beta0_grid_min <- -2.5

#beta0_grid <- seq(beta0_grid_min, beta0_grid_max, length.out = beta0_grid_length - 1)
#beta0_grid <- sort(c(beta0_grid, 0)) 

beta0_grid_length <- 10
#beta0_grid_max <- c(0.25, 0.8, 0.8, 0.8, 0.25, -0.3, 0.8, 0.8, 0.8, 0.8)
#beta0_grid_min <- c(-0.75, -0.2, -0.2, -0.2, -0.75, -1.3, -0.2, -0.2, -0.2, -0.2)
beta0_grid_max <- c(0.75, 0.2, 0.8, 0.8, 0.25, 0.7, 0.8, 0.8, 0.8, 0.8)
beta0_grid_min <- c(-0.25, -0.8, -0.2, -0.2, -0.75, -0.3, -0.2, -0.2, -0.2, -0.2)

#beta1_grid_length <- 10
#beta1_grid_max <- 2
#beta1_grid_min <- -2.5

#beta1_grid <- seq(beta1_grid_min, beta1_grid_max, length.out = beta1_grid_length - 1)
#beta1_grid <- sort(c(beta1_grid, 0)) 

#beta1_grid_length <- 10
beta1_grid_length <- 11
#beta1_grid_max <- c(0.25, -0.8, 0.25, 0.5, 0.25, -0.3, -0.3, -0.3, -0.3, 0.25)
#beta1_grid_min <- c(-0.75, -1.8, -0.75, -0.5, -0.75, -1.3, -1.3, -1.3, -1.3, -0.75)
beta1_grid_max <- c(-0.25, -0.8, 0.25, 0.5, 0.25, -0.3, -0.3, -0.3, -0.3, 0.25)
beta1_grid_min <- c(-1.25, -1.8, -0.75, -0.5, -0.75, -1.3, -1.3, -1.3, -1.3, -0.75)


#beta2_grid_length <- 10
#beta2_grid_max <- 2
#beta2_grid_min <- -2.5

#beta2_grid <- seq(beta2_grid_min, beta2_grid_max, length.out = beta2_grid_length - 1)
#beta2_grid <- sort(c(beta2_grid, 0)) 

beta2_grid_length <- 10
#beta2_grid_max <- c(-0.3, 0.5, -0.8, -0.8, -0.3, 0.25, -0.3, -0.3, -0.3, -0.8)
#beta2_grid_min <- c(-1.3, -0.5, -1.8, -1.8, -1.3, -0.75, -1.3, -1.3, -1.3, -1.8)
beta2_grid_max <- c(-0.75, 0.25, -0.8, -0.8, -0.3, -0.25, -0.3, -0.3, -0.3, -0.8)
beta2_grid_min <- c(-1.75, -0.75, -1.8, -1.8, -1.3, -1.25, -1.3, -1.3, -1.3, -1.8)


GOLAZO_A1A2_sim_results <- foreach(j=1:N, .combine = 'rbind',.packages = c("stats", "golazo", "mvtnorm")) %dopar% {
  
  n <- nrow(train_data[[j]])
  
  #### Estimating lambda ####
  R <- stats::cov2cor(cov(train_data[[j]])) 
  
  beta0_grid <- seq(beta0_grid_min[j], beta0_grid_max[j], length.out = beta0_grid_length)
  beta1_grid <- seq(beta1_grid_min[j], beta1_grid_max[j], length.out = beta1_grid_length)
  beta2_grid <- seq(beta2_grid_min[j], beta2_grid_max[j], length.out = beta2_grid_length)
  
  beta_optimise <- array(NA, dim = c(beta0_grid_length, beta1_grid_length, beta2_grid_length))
  for(b0 in 1:beta0_grid_length)
    for(b1 in 1:beta1_grid_length){
      for(b2 in 1:beta2_grid_length){
        #cat("b0 = ", b0, ", b1 = ", b1, ", b2 = ", b2, "\n")
        try(beta_optimise[b0, b1, b2] <- ebic_eval_two_networks(n, R, A1, A2, beta0 = beta0_grid[b0], beta1 = beta1_grid[b1], beta2 = beta2_grid[b2], ebic.gamma, edge.tol), silent = TRUE)
      }
      cat("b0 = ", b0, ", b1 = ", b1, "DONE", "\n")
    }
  
  min_coord <- which(beta_optimise== min(beta_optimise, na.rm = TRUE), arr.ind = TRUE)
  
  beta_GOLAZO_A1A2_out[1] <- beta0_grid[min_coord[1]]
  beta_GOLAZO_A1A2_out[2] <- beta1_grid[min_coord[2]]
  beta_GOLAZO_A1A2_out[3] <- beta2_grid[min_coord[3]]
  ebic_eval_optim_GOLAZO_A1A2_out <- min(beta_optimise, na.rm = TRUE)
  
  # U <- exp(beta0 + beta1*A1 + beta2*A2) 
  U <- exp(beta_GOLAZO_A1A2_out[1] + beta_GOLAZO_A1A2_out[2]*A1 + beta_GOLAZO_A1A2_out[3]*A2) 
  
  ###################################
  # we are now ready to run GOLAZO and output the optimal K
  diag(U) <- 0
  
  res <- golazo(R, -U, U, tol = 1e-7, verbose=FALSE)
  
  Rho_hat_GOLAZO_A1A2_out <- threshold(cov2cor(res$K), edge.tol)
  
  #out-of-sample log-likelihood
  n_test <- nrow(test_data[[j]])
  
  out_sample_llh_GOLAZO_A1A2 <- 1/n_test*sum(dmvnorm(test_data[[j]], mean = rep(0, p), sigma = cor2cov(cov2cor(solve(Rho_hat_GOLAZO_A1A2_out)), diag(cov(train_data[[j]]))), log = TRUE))
  
  c(beta_GOLAZO_A1A2_out, ebic_eval_optim_GOLAZO_A1A2_out, out_sample_llh_GOLAZO_A1A2)
}

```

## Analysis

```{r GOLAZO_A1A2_diag, include=TRUE,echo=TRUE, eval=TRUE,cache=FALSE}

GOLAZO_A1A2_sim_results

mean(GOLAZO_A1A2_sim_results[,31])
mean(GOLAZO_A1A2_sim_results[,32])

```

# Full Comparison {.tabset}

```{r full_comparison, include=TRUE,echo=TRUE, eval=TRUE,cache=FALSE}

mean(GLASSO_sim_results[,3])
mean(GOLAZO_A1_sim_results[,22])
mean(GOLAZO_A2_sim_results[,22])
mean(GOLAZO_A1A2_sim_results[,32])

GLASSO_sim_results[,2]
GOLAZO_A1_sim_results[,21]
GOLAZO_A2_sim_results[,21]
GOLAZO_A1A2_sim_results[,31]

GOLAZO_A1_sim_results[,21] < GLASSO_sim_results[,2]
GOLAZO_A2_sim_results[,21] < GLASSO_sim_results[,2]
GOLAZO_A1A2_sim_results[,31] <  GOLAZO_A1_sim_results[,21]
GOLAZO_A1A2_sim_results[,31] <  GOLAZO_A2_sim_results[,21]

GLASSO_sim_results[,1]
GOLAZO_A1_sim_results[,1]
GOLAZO_A1_sim_results[,2]
GOLAZO_A2_sim_results[,1]
GOLAZO_A2_sim_results[,2]
GOLAZO_A1A2_sim_results[,1]
GOLAZO_A1A2_sim_results[,2]
GOLAZO_A1A2_sim_results[,3]

## only works for A1A2
GOLAZO_A1A2_sim_results[,1] == beta0_grid_max
GOLAZO_A1A2_sim_results[,1] == beta0_grid_min
GOLAZO_A1A2_sim_results[,2] == beta1_grid_max
GOLAZO_A1A2_sim_results[,2] == beta1_grid_min
GOLAZO_A1A2_sim_results[,3] == beta2_grid_max
GOLAZO_A1A2_sim_results[,3] == beta2_grid_min

mean(GLASSO_sim_results[,3])*round(nrow(covid1)/N_folds)
mean(GOLAZO_A1_sim_results[,22])*round(nrow(covid1)/N_folds)
mean(GOLAZO_A2_sim_results[,22])*round(nrow(covid1)/N_folds)
mean(GOLAZO_A1A2_sim_results[,32])*round(nrow(covid1)/N_folds)

GLASSO_sim_results[,3]
GOLAZO_A1_sim_results[,22]
GOLAZO_A2_sim_results[,22]
GOLAZO_A1A2_sim_results[,32]

sqrt(var(GLASSO_sim_results[,3]))/sqrt(N)
sqrt(var(GOLAZO_A1_sim_results[,22]))/sqrt(N)
sqrt(var(GOLAZO_A2_sim_results[,22]))/sqrt(N)
sqrt(var(GOLAZO_A1A2_sim_results[,32]))/sqrt(N)

```

