---
title: "STOCK Network GLASSO Insample Analysis"
author: "Jack Jewson"
date: "19/07/2022"
output: html_document
---

Here we run the Network GLASSO for the Stock-market data using the Economic and Policy networks

# Preliminaries {.tabset}

## working directory

```{r working_directory, include=TRUE,echo=TRUE, eval=TRUE,cache=FALSE}

data_dir <- '/home/usuario/Documents/Barcelona_Yr1/GraphicalModels_NetworkData/LiLicode/paper_code_github/'

```

## Packages

```{r packages, include=TRUE,echo=TRUE, eval=TRUE,cache=FALSE}
library(readr)
library(devtools)
#install_github("pzwiernik/golazo", build_vignettes=TRUE)
library(golazo)
#source('Network_GLASSO/GOLAZO_function.R')
library(polynom)
library(ggplot2)

library(graphics)
library(xtable)
library(knitr)
```

## Functions 

```{r functions, include=TRUE,echo=TRUE, eval=TRUE,cache=TRUE}

ebic_eval <- function(n, R, U, ebic.gamma, edge.tol){
  res <- golazo(R, L = -U, U = U, verbose = FALSE)
  K <- res$K
  KR <- stats::cov2cor(K)         #to make edge count independend of scalings
  nedg <- length(which(abs(KR[upper.tri(abs(KR), diag = FALSE)]) > edge.tol))
  ## p is the dimensions of R I think - this should be fine but isn't great code!
  ebic <- -(n)*(log(det(K)) - sum(R*K)) + nedg * (log(n) + 4 * ebic.gamma * log(p))
  return(ebic)   
}

ebic_eval_network <- function(n, R, A, beta0, beta1, ebic.gamma, edge.tol){
  U <- exp(beta0 + beta1*A)           #### 
  diag(U) <- 0
  return(ebic_eval(n, R, U, ebic.gamma, edge.tol))
}

ebic_eval_two_networks <- function(n, R, A1, A2, beta0, beta1, beta2, ebic.gamma, edge.tol){
   U <- exp(beta0 + beta1*A1 + beta2*A2)      
   diag(U) <- 0
   return(ebic_eval(n, R, U, ebic.gamma, edge.tol))
}


standardise_network_matrix_tri <- function(A) {
  p <- nrow(A)
  
  A_tri <- A[upper.tri(A)]
  bar_A_tri <- mean(A_tri)
  S2_A_tri <- 1/length(A_tri)*sum((A_tri - bar_A_tri)^2)
  
  return((A - bar_A_tri)/sqrt(S2_A_tri))
}

## Turning the correlation matrix given by the golazo function back to a covariance matrix, useful in out-of-sample-llh
cor2cov <- function(Theta_cor, sigma2_vect){
  # Theta_cor is correlation matrix, sqrt(sigma2_vect) is the standard deviations of each variable
  p <- nrow(Theta_cor)
  Theta_cov <- matrix(NA, nrow = p, ncol = p)
  for(i in 1:p){
    Theta_cov[, i] <- Theta_cor[,i]*sqrt(sigma2_vect[i])*sqrt(sigma2_vect)   
  }
  return(Theta_cov)
}


threshold <- function(Rho_mat, threshold){
  return(Rho_mat*(abs(Rho_mat) >= threshold))
}



## No Network matrix
beta0_max_GLASSO <- function(R){
  return(log(max(abs(R - diag(diag(R))))))## check we can irgnore diags
}


```

## Hyparameters


```{r hyperparameters, include=TRUE,echo=TRUE, eval=TRUE,cache=TRUE}

ebic.gamma <- 0           # set to zero to get BIC
edge.tol <-  1e-6         # be consistent with GLASSO+EBIC method

```

# Data Loading

```{r data_load, include=TRUE,echo=TRUE, eval=TRUE,cache=TRUE}

setwd(data_dir)

stock_trans <- as.matrix(read_csv('Data/Stock/Pre-processed Data/stock_trans.csv'))[, -1]
E_pears <- as.matrix(read_csv('Data/Stock/Pre-processed Data/E_pears.csv'))[, -1]
P_pears <- as.matrix(read_csv('Data/Stock/Pre-processed Data/P_pears.csv'))[, -1]


n <- nrow(stock_trans)
p <- ncol(stock_trans)
N <- 1

```

# GLASSO {.tabset}

## Inference

```{r GLASSO_run, include=TRUE,echo=TRUE, eval=TRUE,cache=TRUE}

L <- matrix(-1,p,p)    
U <- matrix (1,p,p)
diag(U) <- diag(L) <- 0

beta0_GLASSO <-rep(NA, N)
beta0_grid_length <- 20
#beta0_grid_min <- -3
beta0_grid_max <- -1
beta0_grid_min <- -2

beta0_grid <- seq(beta0_grid_min, beta0_grid_max, length.out = beta0_grid_length )


ebic_eval_optim_GLASSO <- rep(NA, N)

time_GLASSO_freq.start <- Sys.time()
for(j in 1:N){
  
  #### Estimating lambda ####
  R <- stats::cov2cor(cov(stock_trans))  
  
  ## grid-search ##
  #beta0_grid_max <- beta0_max_GLASSO(R)
  #beta0_grid <- seq(beta0_grid_min, beta0_grid_max, length.out = beta0_grid_length )
  
  beta_optimise <- rep(NA, beta0_grid_length)
  
  for(b in 1:beta0_grid_length){
    cat("b = ", b, "\n")
    beta_optimise[b] <- ebic_eval(n, R, U = exp(beta0_grid[b])*U, ebic.gamma, edge.tol = edge.tol)
  }
  
  beta0_GLASSO[j] <- beta0_grid[which.min(beta_optimise)]
  ebic_eval_optim_GLASSO[j] <- min(beta_optimise)
  
  #### Using the optimal beta0 ##
  GraphicalModel <- golazo (R, L = exp(beta0_GLASSO[j]) * L, U =exp(beta0_GLASSO[j])* U, tol = 1e-7, verbose=FALSE)
  
  Rho_hat_GLASSO <- threshold(cov2cor(GraphicalModel$K), edge.tol)

}
time_GLASSO_freq.end <- Sys.time()

```

## Analysis

```{r GLASSO_diag, include=TRUE,echo=TRUE, eval=TRUE,cache=FALSE}

beta0_GLASSO # -3.690654  # -1.631706

ebic_eval_optim_GLASSO

sum(Rho_hat_GLASSO[lower.tri((Rho_hat_GLASSO))] != 0)
sum(Rho_hat_GLASSO[lower.tri((Rho_hat_GLASSO))] == 0)


cov2cor(solve(Rho_hat_GLASSO))[1:3, 1:3]
cov2cor(cov(stock_trans))[1:3, 1:3]

time_GLASSO_freq1 <- time_GLASSO_freq.end - time_GLASSO_freq.start
time_GLASSO_freq <- round(time_GLASSO_freq1/N, 3)
time_GLASSO_freq


```

# Motivtaing Plots {.tabset}

## Economic (A1)

```{r Theta_vs_A1, include=TRUE,echo=TRUE, eval=TRUE,cache=TRUE}

A1 <- standardise_network_matrix_tri(E_pears)
diag(A1) <- 0

```

## GLASSO vs A1

```{r GLASSO_vs_A1_1, include=TRUE,echo=TRUE, eval=TRUE,cache=FALSE}

A1_plot <- A1[upper.tri(A1)]

partial_corr_GLASSO <- - Rho_hat_GLASSO[upper.tri(Rho_hat_GLASSO)]

plot(x = A1_plot, y = partial_corr_GLASSO, xlab = "Economic Index (Pearson's Correlation)", ylab ="Partial Correlation (GLASSO)")

```


```{r GLASSO_vs_A1_2, include=TRUE,echo=TRUE, eval=TRUE,cache=FALSE}

## Binning the network - 
library(dplyr)
num_bins <- 10

# Quantile bins - Equi-obs bins
df_A1_plot <- data.frame(A1_plot)

df_A1_plot <- df_A1_plot %>% mutate(A1_plot_bin = cut(A1_plot, 
                                                      breaks = unique(quantile(A1_plot, probs=seq.int(0,1, by=1/num_bins))), 
                                                      include.lowest=TRUE))
df_A1_plot <- df_A1_plot %>% mutate(A1_plot_bin_cat = ntile(A1_plot, num_bins))
df_A1_plot <- df_A1_plot %>% mutate(partial_corr_GLASSO = partial_corr_GLASSO)

plot(aggregate(df_A1_plot$A1_plot, list(df_A1_plot$A1_plot_bin_cat), mean)$x, log(aggregate(df_A1_plot$partial_corr_GLASSO^2, list(df_A1_plot$A1_plot_bin_cat), mean)$x), xlab = "A1 - bin mid-point", ylab = "log E[rho_ij | A1 binned]", main = "Quantile (Equi-obs) bins")

df_plot <- data.frame(A1_bin_mean = aggregate(df_A1_plot$A1_plot, list(df_A1_plot$A1_plot_bin_cat), mean)$x, 
                      Mean_r_ij2 = aggregate(df_A1_plot$partial_corr_GLASSO^2, list(df_A1_plot$A1_plot_bin_cat), mean)$x, 
                      SE_r_ij2 = sqrt(aggregate(df_A1_plot$partial_corr_GLASSO^2, list(df_A1_plot$A1_plot_bin_cat), var)$x)/sqrt(aggregate(df_A1_plot$partial_corr_GLASSO^2, list(df_A1_plot$A1_plot_bin_cat), length)$x))

plot1 <- ggplot(df_plot, aes(x=A1_bin_mean, y=log(Mean_r_ij2))) + 
  geom_pointrange(aes(ymin = log(Mean_r_ij2 - SE_r_ij2), ymax = log(Mean_r_ij2 + SE_r_ij2)), position=position_dodge(0.05)) +
  ggtitle("Quantile (Equi-obs) bins") + 
  labs(y = "log E[rho_ij | A1 binned]", x = "A1 - bin mid-point")
print(plot1)

# Equi-width bins
df_A1_plot <- data.frame(A1_plot)
Equi_bins_breaks <- seq(min(A1_plot), max(A1_plot), length.out = num_bins + 1)
A1_plot_bin_mid = (Equi_bins_breaks[1:num_bins] + Equi_bins_breaks[2:(num_bins + 1)])/2

df_A1_plot <- df_A1_plot %>% mutate(A1_plot_bin = cut(A1_plot, 
                                                      breaks = Equi_bins_breaks, 
                                                      include.lowest=TRUE))
df_A1_plot <- df_A1_plot %>% mutate(partial_corr_GLASSO = partial_corr_GLASSO)


plot(A1_plot_bin_mid, log(aggregate(df_A1_plot$partial_corr_GLASSO^2, list(df_A1_plot$A1_plot_bin), mean)$x), xlab = "A1 - bin mid-point", ylab = "log E[rho_ij | A1 binned]", main = "Equi-spaced bins")


df_plot <- data.frame(A1_bin_mean = A1_plot_bin_mid, 
                      Mean_r_ij2 = aggregate(df_A1_plot$partial_corr_GLASSO^2, list(df_A1_plot$A1_plot_bin), mean)$x, 
                      SE_r_ij2 = sqrt(aggregate(df_A1_plot$partial_corr_GLASSO^2, list(df_A1_plot$A1_plot_bin), var)$x)/sqrt(aggregate(df_A1_plot$partial_corr_GLASSO^2, list(df_A1_plot$A1_plot_bin), length)$x))


plot1 <- ggplot(df_plot, aes(x=A1_bin_mean, y=log(Mean_r_ij2))) + 
  geom_pointrange(aes(ymin = log(Mean_r_ij2 - SE_r_ij2), ymax = log(Mean_r_ij2 + SE_r_ij2)), position=position_dodge(0.05)) +
  ggtitle("Equi-spaced bins") + 
  labs(y = "log E[rho_ij | A1 binned]", x = "A1 - bin mid-point")
print(plot1)

```

## Policy (A2)

```{r Theta_vs_A2, include=TRUE,echo=TRUE, eval=TRUE,cache=TRUE}

A2 <- standardise_network_matrix_tri(P_pears)
diag(A2) <- 0


```

## GLASSO vs A2

```{r GLASSO_vs_A2_1, include=TRUE,echo=TRUE, eval=TRUE,cache=FALSE}

A2_plot <- A2[upper.tri(A2)]

partial_corr_GLASSO <- - Rho_hat_GLASSO[upper.tri(Rho_hat_GLASSO)]

plot(x = A2_plot, y = partial_corr_GLASSO, xlab = "Policy Index (Pearson's Correlation)", ylab ="Partial Correlation (GLASSO)")


cor(as.vector(A1_plot), as.vector(A2_plot))
```

```{r GLASSO_vs_A2_2, include=TRUE,echo=TRUE, eval=TRUE,cache=FALSE}

## Binning the network - 
library(dplyr)
num_bins <- 10

# Quantile bins - Equi-obs bins
df_A2_plot <- data.frame(A2_plot)

df_A2_plot <- df_A2_plot %>% mutate(A2_plot_bin = cut(A2_plot, 
                                                      breaks = unique(quantile(A2_plot, probs=seq.int(0,1, by=1/num_bins))), 
                                                      include.lowest=TRUE))
df_A2_plot <- df_A2_plot %>% mutate(A2_plot_bin_cat = ntile(A2_plot, num_bins))
df_A2_plot <- df_A2_plot %>% mutate(partial_corr_GLASSO = partial_corr_GLASSO)

plot(aggregate(df_A2_plot$A2_plot, list(df_A2_plot$A2_plot_bin_cat), mean)$x, log(aggregate(df_A2_plot$partial_corr_GLASSO^2, list(df_A2_plot$A2_plot_bin_cat), mean)$x), xlab = "A2 - bin mid-point", ylab = "log E[rho_ij^2 | A2 binned]", main = "Quantile (Equi-obs) bins")

df_plot <- data.frame(A2_bin_mean = aggregate(df_A2_plot$A2_plot, list(df_A2_plot$A2_plot_bin_cat), mean)$x, 
                      Mean_r_ij2 = aggregate(df_A2_plot$partial_corr_GLASSO^2, list(df_A2_plot$A2_plot_bin_cat), mean)$x, 
                      SE_r_ij2 = sqrt(aggregate(df_A2_plot$partial_corr_GLASSO^2, list(df_A2_plot$A2_plot_bin_cat), var)$x)/sqrt(aggregate(df_A2_plot$partial_corr_GLASSO^2, list(df_A2_plot$A2_plot_bin_cat), length)$x))

plot1 <- ggplot(df_plot, aes(x=A2_bin_mean, y=log(Mean_r_ij2))) + 
  geom_pointrange(aes(ymin = log(Mean_r_ij2 - SE_r_ij2), ymax = log(Mean_r_ij2 + SE_r_ij2)), position=position_dodge(0.05)) +
  ggtitle("Quantile (Equi-obs) bins") + 
  labs(y = "log E[rho_ij^2 | A2 binned]", x = "A2 - bin mid-point")
print(plot1)

# Equi-width bins
df_A2_plot <- data.frame(A2_plot)
Equi_bins_breaks <- seq(min(A2_plot), max(A2_plot), length.out = num_bins + 1)
A2_plot_bin_mid = (Equi_bins_breaks[1:num_bins] + Equi_bins_breaks[2:(num_bins + 1)])/2

df_A2_plot <- df_A2_plot %>% mutate(A2_plot_bin = cut(A2_plot, 
                                                      breaks = Equi_bins_breaks, 
                                                      include.lowest=TRUE))
df_A2_plot <- df_A2_plot %>% mutate(partial_corr_GLASSO = partial_corr_GLASSO)


plot(A2_plot_bin_mid, log(aggregate(df_A2_plot$partial_corr_GLASSO^2, list(df_A2_plot$A2_plot_bin), mean)$x), xlab = "A2 - bin mid-point", ylab = "log E[rho_ij^2 | A2 binned]", main = "Equi-spaced bins")


df_plot <- data.frame(A2_bin_mean = A2_plot_bin_mid, 
                      Mean_r_ij2 = aggregate(df_A2_plot$partial_corr_GLASSO^2, list(df_A2_plot$A2_plot_bin), mean)$x, 
                      SE_r_ij2 = sqrt(aggregate(df_A2_plot$partial_corr_GLASSO^2, list(df_A2_plot$A2_plot_bin), var)$x)/sqrt(aggregate(df_A2_plot$partial_corr_GLASSO^2, list(df_A2_plot$A2_plot_bin), length)$x))


plot1 <- ggplot(df_plot, aes(x=A2_bin_mean, y=log(Mean_r_ij2))) + 
  geom_pointrange(aes(ymin = log(Mean_r_ij2 - SE_r_ij2), ymax = log(Mean_r_ij2 + SE_r_ij2)), position=position_dodge(0.05)) +
  ggtitle("Equi-spaced bins") + 
  labs(y = "log E[rho_ij | A2 binned]", x = "A2 - bin mid-point")
print(plot1)

```


# GOLAZO - Economic (A1) {.tabset}

## Inference

```{r GOLAZO_A1, include=TRUE,echo=TRUE, eval=TRUE,cache=TRUE}

L <- matrix(-1,p,p)    
U <- matrix (1,p,p)
diag(U) <- diag(L) <- 0

beta_GOLAZO_A1_full <- matrix(NA, nrow = N, ncol = 2)

#beta0_grid_length <- 20
#beta0_grid_max <- 2
#beta0_grid_min <- -5

#beta0_grid <- seq(beta0_grid_min, beta0_grid_max, length.out = beta0_grid_length - 1)
#beta0_grid <- sort(c(beta0_grid, 0)) 

beta0_grid_length <- 20
beta0_grid_max <- -0.5
beta0_grid_min <- -2

beta0_grid <- seq(beta0_grid_min, beta0_grid_max, length.out = beta0_grid_length)

#beta1_grid_length <- 20
#beta1_grid_max <- 2
#beta1_grid_min <- -5

#beta1_grid <- seq(beta1_grid_min, beta1_grid_max, length.out = beta1_grid_length - 1)
#beta1_grid <- sort(c(beta1_grid, 0)) 

beta1_grid_length <- 21
beta1_grid_max <- 0.5
beta1_grid_min <- -1

beta1_grid <- seq(beta1_grid_min, beta1_grid_max, length.out = beta1_grid_length - 1)
beta1_grid <- sort(c(beta1_grid, 0)) 

ebic_eval_optim_GOLAZO_A1_full <- rep(NA, N)


time_GOLAZO_A1_freq.start <- Sys.time()
for(j in 1:N){
  
  #### Estimating lambda ####
  R <- stats::cov2cor(cov(stock_trans)) 
  
  beta_optimise <- matrix(NA, nrow = beta0_grid_length, ncol = beta1_grid_length)
  for(b0 in 1:beta0_grid_length){
    for(b1 in 1:beta1_grid_length){
      #cat("b0 = ", b0, ", b1 = ", b1, "\n")
      try(beta_optimise[b0, b1] <- ebic_eval_network(n, R, A1, beta0 = beta0_grid[b0], beta1 = beta1_grid[b1], ebic.gamma, edge.tol), silent = TRUE)
    }
    cat("b0 = ", b0, "DONE", "\n")
  }
  
  min_coord <- which(beta_optimise== min(beta_optimise, na.rm = TRUE), arr.ind = TRUE)
  
  beta_GOLAZO_A1_full[j, 1] <- beta0_grid[min_coord[1]]
  beta_GOLAZO_A1_full[j, 2] <- beta1_grid[min_coord[2]]
  ebic_eval_optim_GOLAZO_A1_full[j] <- min(beta_optimise, na.rm = TRUE)
  
  # U <- exp(beta0 + beta1*A1) 
  U <- exp(beta_GOLAZO_A1_full[j,1] + beta_GOLAZO_A1_full[j,2]*A1) 
  
  ###################################
  # we are now ready to run GOLAZO and output the optimal K
  diag(U) <- 0
  
  res <- golazo(R, -U, U, tol = 1e-7, verbose=FALSE)
  Rho_hat_GOLAZO_A1_full <- threshold(cov2cor(res$K), edge.tol)
}
time_GOLAZO_A1_freq.end <- Sys.time()
```

## Analysis

```{r GOLAZO_A1_diag, include=TRUE,echo=TRUE, eval=TRUE,cache=FALSE}

beta_GOLAZO_A1_full

ebic_eval_optim_GOLAZO_A1_full

sum(Rho_hat_GOLAZO_A1_full[lower.tri((Rho_hat_GOLAZO_A1_full))] != 0) # 1813 # 596 #540 
sum(Rho_hat_GOLAZO_A1_full[lower.tri((Rho_hat_GOLAZO_A1_full))] == 0) # 3038 # 4255 # 4311

## ploting the EBIC in beta0 and beta1
library(graphics)
contour(beta0_grid, beta1_grid, beta_optimise, xlab = "beta0", ylab = "beta1")
points(beta_GOLAZO_A1_full[1], beta_GOLAZO_A1_full[2], col = "red", pch = 4, cex = 1.5, lwd = 3)

time_GOLAZO_A1_freq1 <- time_GOLAZO_A1_freq.end - time_GOLAZO_A1_freq.start
time_GOLAZO_A1_freq <- round(time_GOLAZO_A1_freq1/N, 3)
time_GOLAZO_A1_freq

```

# GOLAZO - Facebook (A2) {.tabset}

## Inference

```{r GOLAZO_A2, include=TRUE,echo=TRUE, eval=TRUE,cache=TRUE}

L <- matrix(-1,p,p)    
U <- matrix (1,p,p)
diag(U) <- diag(L) <- 0

beta_GOLAZO_A2_full <- matrix(NA, nrow = N, ncol = 2)

#beta0_grid_length <- 20
#beta0_grid_max <- 2
#beta0_grid_min <- -5

#beta0_grid <- seq(beta0_grid_min, beta0_grid_max, length.out = beta0_grid_length - 1)
#beta0_grid <- sort(c(beta0_grid, 0))

beta0_grid_length <- 20
beta0_grid_max <- 0
beta0_grid_min <- -1.5

beta0_grid <- seq(beta0_grid_min, beta0_grid_max, length.out = beta0_grid_length)

#beta2_grid_length <- 20
#beta2_grid_max <- 2
#beta2_grid_min <- -5

#beta2_grid <- seq(beta2_grid_min, beta2_grid_max, length.out = beta2_grid_length - 1)
#beta2_grid <- sort(c(beta2_grid, 0)) 

beta2_grid_length <- 20
beta2_grid_max <- 0
beta2_grid_min <- -1.5

beta2_grid <- seq(beta2_grid_min, beta2_grid_max, length.out = beta2_grid_length)

ebic_eval_optim_GOLAZO_A2_full <- rep(NA, N)

time_GOLAZO_A2_freq.start <- Sys.time()
for(j in 1:N){
  
  #### Estimating lambda ####
  R <- stats::cov2cor(cov(stock_trans)) 
  
  beta_optimise <- matrix(NA, nrow = beta0_grid_length, ncol = beta2_grid_length)
  for(b0 in 1:beta0_grid_length){
    for(b1 in 1:beta2_grid_length){
      #cat("b0 = ", b0, ", b1 = ", b1, "\n")
      try(beta_optimise[b0, b1] <- ebic_eval_network(n, R, A2, beta0 = beta0_grid[b0], beta1 = beta2_grid[b1], ebic.gamma, edge.tol), silent = TRUE)
    }
    cat("b0 = ", b0, "DONE", "\n")
  }
  
  min_coord <- which(beta_optimise== min(beta_optimise, na.rm = TRUE), arr.ind = TRUE)
  
  beta_GOLAZO_A2_full[j, 1] <- beta0_grid[min_coord[1]]
  beta_GOLAZO_A2_full[j, 2] <- beta2_grid[min_coord[2]]
  ebic_eval_optim_GOLAZO_A2_full[j] <- min(beta_optimise, na.rm = TRUE)
  
  # U <- exp(beta0 + beta2*A2) 
  U <- exp(beta_GOLAZO_A2_full[j,1] + beta_GOLAZO_A2_full[j,2]*A2) 
  
  ###################################
  # we are now ready to run GOLAZO and output the optimal K
  diag(U) <- 0
  
  res <- golazo(R, -U, U, tol = 1e-7, verbose=FALSE)
  Rho_hat_GOLAZO_A2_full <- threshold(cov2cor(res$K), edge.tol)
}
time_GOLAZO_A2_freq.end <- Sys.time()

```

## Analysis

```{r GOLAZO_A2_diag, include=TRUE,echo=TRUE, eval=TRUE,cache=FALSE}

beta_GOLAZO_A2_full

ebic_eval_optim_GOLAZO_A2_full

sum(Rho_hat_GOLAZO_A2_full[lower.tri((Rho_hat_GOLAZO_A2_full))] != 0) # 1813 # 596 #540 
sum(Rho_hat_GOLAZO_A2_full[lower.tri((Rho_hat_GOLAZO_A2_full))] == 0) # 3038 # 4255 # 4311

## ploting the EBIC in beta0 and beta2
contour(beta0_grid, beta2_grid, beta_optimise, xlab = "beta0", ylab = "beta2")
points(beta_GOLAZO_A2_full[1], beta_GOLAZO_A2_full[2], col = "red", pch = 4, cex = 1.5, lwd = 3)

### Plotting the fitted partial correlations against the network

A2_plot <- A2[upper.tri(A2)]

partial_corr_GOLAZO_A2_full  <- - Rho_hat_GOLAZO_A2_full[upper.tri(Rho_hat_GOLAZO_A2_full)]

none_na_plot <- which(log(partial_corr_GOLAZO_A2_full^2)!=-Inf)

plot(x = A2_plot[none_na_plot], y = log(partial_corr_GOLAZO_A2_full^2)[none_na_plot], xlab = "log(Facebook Connection)", ylab ="log(r^2)", main = "GOLAZO A2 estimated")
l <- loess(log(partial_corr_GOLAZO_A2_full^2)[none_na_plot] ~ A2_plot[none_na_plot])
o <- order(l$x)
lines(l$x[o], l$fitted[o], col='red')

time_GOLAZO_A2_freq1 <- time_GOLAZO_A2_freq.end - time_GOLAZO_A2_freq.start
time_GOLAZO_A2_freq <- round(time_GOLAZO_A2_freq1/N, 3)
time_GOLAZO_A2_freq

```

# GOLAZO - Economic & Policy (A1 & A2) {.tabset}

## Inference

```{r GOLAZO_A1A2, include=TRUE,echo=TRUE, eval=TRUE,cache=TRUE}

L <- matrix(-1,p,p)    
U <- matrix (1,p,p)
diag(U) <- diag(L) <- 0


beta_GOLAZO_A1A2_full <- matrix(NA, nrow = N, ncol = 3)

#beta0_grid_length <- 10
#beta0_grid_max <- 2
#beta0_grid_min <- -2.5

#beta0_grid <- seq(beta0_grid_min, beta0_grid_max, length.out = beta0_grid_length - 1)
#beta0_grid <- sort(c(beta0_grid, 0)) 

beta0_grid_length <- 10
beta0_grid_max <- -1
beta0_grid_min <- -2

beta0_grid <- seq(beta0_grid_min, beta0_grid_max, length.out = beta0_grid_length)

#beta1_grid_length <- 10
#beta1_grid_max <- 2
#beta1_grid_min <- -2.5

#beta1_grid <- seq(beta1_grid_min, beta1_grid_max, length.out = beta1_grid_length - 1)
#beta1_grid <- sort(c(beta1_grid, 0)) 

beta1_grid_length <- 11
beta1_grid_max <- 0.25
beta1_grid_min <- -0.75

beta1_grid <- seq(beta1_grid_min, beta1_grid_max, length.out = beta1_grid_length - 1)
# JACK: want to make sure we try at 0
beta1_grid <- sort(c(beta1_grid, 0)) 

#beta2_grid_length <- 10
#beta2_grid_max <- 2
#beta2_grid_min <- -2.5

#beta2_grid <- seq(beta2_grid_min, beta2_grid_max, length.out = beta2_grid_length - 1)
#beta2_grid <- sort(c(beta2_grid, 0)) 

beta2_grid_length <- 11
beta2_grid_max <- 0.5
beta2_grid_min <- -0.5

beta2_grid <- seq(beta2_grid_min, beta2_grid_max, length.out = beta2_grid_length - 1)
# JACK: want to make sure we try at 0
beta2_grid <- sort(c(beta2_grid, 0)) 

ebic_eval_optim_GOLAZO_A1A2_full <- rep(NA, N)

time_GOLAZO_A1A2_freq.start <- Sys.time()
for(j in 1:N){
  
  #### Estimating lambda ####
  R <- stats::cov2cor(cov(stock_trans)) 
  
  beta_optimise <- array(NA, dim = c(beta0_grid_length, beta1_grid_length, beta2_grid_length))
  for(b0 in 1:beta0_grid_length)
    for(b1 in 1:beta1_grid_length){
      for(b2 in 1:beta2_grid_length){
        #cat("b0 = ", b0, ", b1 = ", b1, ", b2 = ", b2, "\n")
        try(beta_optimise[b0, b1, b2] <- ebic_eval_two_networks(n, R, A1, A2, beta0 = beta0_grid[b0], beta1 = beta1_grid[b1], beta2 = beta2_grid[b2], ebic.gamma, edge.tol), silent = TRUE)
      }
      cat("b0 = ", b0, ", b1 = ", b1, "DONE", "\n")
    }
  
  min_coord <- which(beta_optimise== min(beta_optimise, na.rm = TRUE), arr.ind = TRUE)
  
  beta_GOLAZO_A1A2_full[j, 1] <- beta0_grid[min_coord[1]]
  beta_GOLAZO_A1A2_full[j, 2] <- beta1_grid[min_coord[2]]
  beta_GOLAZO_A1A2_full[j, 3] <- beta2_grid[min_coord[3]]
  ebic_eval_optim_GOLAZO_A1A2_full[j] <- min(beta_optimise, na.rm = TRUE)
  
  # U <- exp(beta0 + beta1*A1 + beta2*A2) 
  U <- exp(beta_GOLAZO_A1A2_full[j,1] + beta_GOLAZO_A1A2_full[j,2]*A1 + beta_GOLAZO_A1A2_full[j,3]*A2) 
  
  ###################################
  # we are now ready to run GOLAZO and output the optimal K
  diag(U) <- 0
  
  res <- golazo(R, -U, U, tol = 1e-7, verbose=FALSE)
  
  Rho_hat_GOLAZO_A1A2_full <- threshold(cov2cor(res$K), edge.tol)
}
time_GOLAZO_A1A2_freq.end <- Sys.time()

```

## Analysis

```{r GOLAZO_A1A2_diag, include=TRUE,echo=TRUE, eval=TRUE,cache=FALSE}

beta_GOLAZO_A1A2_full

ebic_eval_optim_GOLAZO_A1A2_full

sum(Rho_hat_GOLAZO_A1A2_full[lower.tri((Rho_hat_GOLAZO_A1A2_full))] != 0)
sum(Rho_hat_GOLAZO_A1A2_full[lower.tri((Rho_hat_GOLAZO_A1A2_full))] == 0)

beta_optimise_plot <- beta_optimise

## ploting the EBIC in Bivariate Marginals - need to marginalise
contour(beta1_grid, beta2_grid, apply(beta_optimise_plot, MARGIN = c(2, 3), FUN = function(x){mean(x, na.rm = TRUE)}), xlab = "beta1", ylab = "beta2")
points(beta_GOLAZO_A1A2_full[2], beta_GOLAZO_A1A2_full[3], col = "red", pch = 4, cex = 1.5, lwd = 3)

contour(beta0_grid, beta1_grid, apply(beta_optimise_plot, MARGIN = c(1, 2), FUN = function(x){mean(x, na.rm = TRUE)}), xlab = "beta0", ylab = "beta1")
points(beta_GOLAZO_A1A2_full[1], beta_GOLAZO_A1A2_full[2], col = "red", pch = 4, cex = 1.5, lwd = 3)

contour(beta0_grid, beta2_grid, apply(beta_optimise_plot, MARGIN = c(1, 3), FUN = function(x){mean(x, na.rm = TRUE)}), xlab = "beta0", ylab = "beta2")
points(beta_GOLAZO_A1A2_full[1], beta_GOLAZO_A1A2_full[3], col = "red", pch = 4, cex = 1.5, lwd = 3)

## fixing the missing at it's optimum
## ploting the EBIC in Bivariate Marginals - need to marginalise
contour(beta1_grid, beta2_grid, beta_optimise_plot[min_coord[1],,], xlab = "beta1", ylab = "beta2", main = "beta0 = hat_beta0")
points(beta_GOLAZO_A1A2_full[2], beta_GOLAZO_A1A2_full[3], col = "red", pch = 4, cex = 1.5, lwd = 3)

contour(beta0_grid, beta1_grid, beta_optimise_plot[,,min_coord[3]], xlab = "beta0", ylab = "beta1", main = "beta2 = hat_beta2")
points(beta_GOLAZO_A1A2_full[1], beta_GOLAZO_A1A2_full[2], col = "red", pch = 4, cex = 1.5, lwd = 3)

contour(beta0_grid, beta2_grid, beta_optimise_plot[,min_coord[2],], xlab = "beta0", ylab = "beta2", main = "beta1 = hat_beta1")
points(beta_GOLAZO_A1A2_full[1], beta_GOLAZO_A1A2_full[3], col = "red", pch = 4, cex = 1.5, lwd = 3)

## Close to the minimum 

n_close <- 10
beta_close <- matrix(NA, nrow = n_close, ncol = 3)
for(k in 1:n_close){
  min_close_coord <- which(beta_optimise == (sort(beta_optimise)[k]), arr.ind = TRUE)
  
  beta_close[k, 1] <- beta0_grid[min_close_coord[1]]
  beta_close[k, 2] <- beta1_grid[min_close_coord[2]]
  beta_close[k, 3] <- beta2_grid[min_close_coord[3]]
}

beta_close
sort(beta_optimise)[1:n_close]

time_GOLAZO_A1A2_freq1 <- time_GOLAZO_A1A2_freq.end - time_GOLAZO_A1A2_freq.start
time_GOLAZO_A1A2_freq <- round(time_GOLAZO_A1A2_freq1/N, 3)
time_GOLAZO_A1A2_freq

```

# Full Comparison {.tabset}

```{r full_comparison, include=TRUE,echo=TRUE, eval=TRUE,cache=FALSE}

ebic_eval_optim_GLASSO
ebic_eval_optim_GOLAZO_A1_full
ebic_eval_optim_GOLAZO_A2_full
ebic_eval_optim_GOLAZO_A1A2_full

beta0_GLASSO
beta_GOLAZO_A1_full
beta_GOLAZO_A2_full
beta_GOLAZO_A1A2_full


## BIC adjusted
ebic_eval_optim_GLASSO
ebic_eval_optim_GOLAZO_A1_full + (log(n) + 4 * ebic.gamma * log(p))
ebic_eval_optim_GOLAZO_A2_full + (log(n) + 4 * ebic.gamma * log(p))
ebic_eval_optim_GOLAZO_A1A2_full + 2*(log(n) + 4 * ebic.gamma * log(p))

options(xtable.floating = FALSE)
options(xtable.timestamp = "")

table_frame_freq <- data.frame("Method" = c("GLASSO", "GOLAZO - A1", "GOLAZO - A2", "GOLAZO - A1 & A2"), 
                               "EBIC" = c(ebic_eval_optim_GLASSO, 
                                          ebic_eval_optim_GOLAZO_A1_full + (log(n) + 4 * ebic.gamma * log(p)),
                                          ebic_eval_optim_GOLAZO_A2_full + (log(n) + 4 * ebic.gamma * log(p)),
                                          ebic_eval_optim_GOLAZO_A1A2_full + 2*(log(n) + 4 * ebic.gamma * log(p))),
                               "hat{beta}_0" = c(beta0_GLASSO, 
                                                 beta_GOLAZO_A1_full[,1],
                                                 beta_GOLAZO_A2_full[,1],
                                                 beta_GOLAZO_A1A2_full[,1]),
                               "hat{beta}_1" = c(NA, 
                                                 beta_GOLAZO_A1_full[,2],
                                                 NA, 
                                                 beta_GOLAZO_A1A2_full[,2]), 
                               "hat{beta}_2" = c(NA, 
                                                 NA, 
                                                 beta_GOLAZO_A2_full[,2], 
                                                 beta_GOLAZO_A1A2_full[,3]),
                               "Edges" = c(
                            sum(Rho_hat_GLASSO[lower.tri((Rho_hat_GLASSO))] != 0),     
                            sum(Rho_hat_GOLAZO_A1_full[lower.tri((Rho_hat_GOLAZO_A1_full))] != 0),   
                            sum(Rho_hat_GOLAZO_A2_full[lower.tri((Rho_hat_GOLAZO_A2_full))] != 0),     
                            sum(Rho_hat_GOLAZO_A1A2_full[lower.tri((Rho_hat_GOLAZO_A1A2_full))] != 0)),
                               "Non-Edges" = c(
                            sum(Rho_hat_GLASSO[lower.tri((Rho_hat_GLASSO))] == 0),     
                            sum(Rho_hat_GOLAZO_A1_full[lower.tri((Rho_hat_GOLAZO_A1_full))] == 0),    
                            sum(Rho_hat_GOLAZO_A2_full[lower.tri((Rho_hat_GOLAZO_A2_full))] == 0),     
                            sum(Rho_hat_GOLAZO_A1A2_full[lower.tri((Rho_hat_GOLAZO_A1A2_full))] == 0))
                              )
xtable(table_frame_freq, digits=3)

kable(table_frame_freq)

```


